---
title: "Models"
author: "Thea Rolskov Sloth"
date: "15/10/2019"
output: html_document
---

#Getting packages
```{r loading packages, include = FALSE}
library(pacman)
p_load(brms, tidyverse, tidybayes, ggplot2, LaplacesDemon, rethinking, tidyr, reshape2, tibble, plotly, jpeg, tm, ggrepel, utils, boot, Hmisc, scales, gridExtra)
```

#Setting directory
```{r}
setwd("~/Bachelor-MM-/") #TRS
```

#Loading data
```{r}
data_ib <- read.csv("implicit_bias/data_ib.csv")[,2:12]
data_eb <- read.csv("explicit_bias/eb_results.csv")[, 2:6]
data_db <- read.csv("decision_bias/disagree_sensitivity_db_long.csv")[, 2:44]
data_db_all <- read.csv("decision_bias/data_db_all.csv")
```


#IMPLICIT BIAS

##Difference between gender and condition, interaction
```{r model, condition * gender}

#Tranforming condition to a factor
data_ib$condition <- as.factor(data_ib$condition)
#to figure out which prior I need to make 
get_prior(rt ~  condition*gender + (condition|ID), data = data_ib)

#Defining a prior
prior_ib2 = c(prior(normal(-0.4, 0.2), class = "Intercept"),
              prior(normal(0, 0.2), class = "b"),
              prior(normal(0, 0.2), class = "sigma"),
              prior(normal(0, 0.1), class = "sd"))

#Implicit model
model_ib2_prior <- brm(rt_log ~ condition*gender + (condition|ID),
                    data = data_ib,
                    family = gaussian(),
                    prior = prior_ib2,
                    sample_prior = "only",
                    seed = 123,
                    cores = 2,
                    chains = 2)

pp_check(model_ib2_prior, nsamples = 100) #Doing a predictive prior check to test priors


model_ib2 <- brm(rt_log ~ condition*gender + (condition|ID),
                    data = data_ib,
                    family = gaussian(),
                    prior = prior_ib2,
                    sample_prior = TRUE,
                    seed = 123,
                    iter = 5000,
                    warmup = 2000,
                    cores = 4,
                    chains = 4)

summary(model_ib2) 

#plotting
marginal_effects(model_ib2)

plot(model_ib2)

effective_sample(model_ib2)
```



##Hypothesis testing
###H2.1
```{r}
hypothesis(model_ib2, "(Intercept + genderMale)/2 > ((Intercept + condition1)+(Intercept + condition1+genderMale+condition1:genderMale)/2)")



```

#H2.2
```{r}
hypothesis(model_ib2, "condition1 = condition1 + condition1:genderMale")


```

##Plotting, implicit bias


###H2.1 and H2.2
```{r prepare predictions}
nd_ib2 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 10),
         ID = NA, 
         condition=factor(0:1) %>% 
           rep(., times = 10)))

nd_ib2$gender <- ifelse(nd_ib2$gender == 0, "Male", "Female")

pred_ib2 <-
  predict(model_ib2, newdata = nd_ib2) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_ib2)

pred_ib2$Estimate_sec <- exp(pred_ib2$Estimate)

pred_ib2$dif <- NA
pred_ib2$dif[pred_ib2$gender == "Male"] <- pred_ib2$Estimate[pred_ib2$condition == 1 & pred_ib2$gender == "Male"] - pred_ib2$Estimate[pred_ib2$condition == 0 & pred_ib2$gender == "Male"]

pred_ib2$dif[pred_ib2$gender == "Female"] <- pred_ib2$Estimate[pred_ib2$condition == 1 & pred_ib2$gender == "Female"] - pred_ib2$Estimate[pred_ib2$condition == 0 & pred_ib2$gender == "Female"]

pred_ib2_mean <- pred_ib2 %>% group_by(condition, gender) %>% summarise(mean_prediction = mean(Estimate))

pred_ib2$condition <- ifelse(pred_ib2$condition == 0, "Congruent", "Incongruent")


```


```{r H2.2 plot}
#create the plot
H2.2.1 <- ggplot(pred_ib2, aes(x = gender, y = dif, fill = gender)) +
  labs(x = "Gender", y = "Difference in reaction time (log)", title = "Hypothesis 2.2.1") +
  geom_bar(stat="summary", position = position_dodge2(), alpha = 0.6)  + 
 #stat_summary(fun.data = "mean_cl_boot", colour = "red") +
  geom_errorbar(aes(ymin=0, ymax=(mean(dif) + mean(Est.Error))),width=.2,position=position_dodge(.9)) + 
  #geom_point(aes(x = condition, y = Estimate_prop, fill = gender), data = pred_ib2, size = 2, position = position_dodge2(width= 0.1)) + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(text = element_text(size=20))


H2.2.1


pred_ib2$gender <- as.factor(pred_ib2$gender)

H_ib_interaction <- ggplot(pred_ib2, aes(x = condition, y = Estimate_sec, fill = gender)) + 
  geom_violin(aes(x = condition, y = Estimate_sec), data = pred_ib2, width = 0.7, alpha = 0.6) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Condition", y = "Reaction time (seconds)", title = "Hypothesis 2.1 and 2.2") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Gender") + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_y_continuous(labels=scales::number_format(accuracy = 0.01, decimal.mark = '.')) + 
  theme(text = element_text(size=20))
  
 

H_ib_interaction


```


```{r}

(y+runif(100, -1, -0.5))

#plot with lines 
H2.2.1_lines <- ggplot(pred_ib2, aes(x = condition, y = Estimate_sec, group = gender, color = gender)) + 
  scale_color_manual(values=c("orange", "blue"), name = "Gender") + 
  #stat_summary(fun.data = "mean_cl_boot", color = "black", size = 1.5, geom = "point") +
  stat_summary(fun.y = mean, geom="line") + 
  
  labs(x = "Condition", y = "Reaction time (seconds)", title = "Hypothesis 2.2") + 
  theme(plot.title = element_text(hjust = 0.5)) 
H2.2.1_lines

```



#EXPLICIT BIAS

Lav en model, der viser om mænd er mere sexistiske. 
Men det informerer ikkke spørgsmålet, om der et kønsbias synderligt, det den kun er rettet imod at beskrive kønnenes indstilling til kvinder?  

##Overall_score

```{r overall score, models}
#to figure out which prior we need to make
get_prior(overall_score ~ gender + (1|ID), data = data_eb)

#Defining a prior, mean set to 2.5 because best conceptual meaning
prior_eb1.1 = c(prior(normal(2.5, 0.5), class = "Intercept"), 
          prior(normal(0, 0.5), class = "b"), 
          prior(normal(0, 0.5), class = "sigma"),
          prior(normal(0, 0.1), class = "sd"))

#try and make a prior with mean set to 2 as it might make the model better
prior_eb1.2 = c(prior(normal(2, 0.5), class = "Intercept"), 
          prior(normal(0, 0.5), class = "b"), 
          prior(normal(0, 0.5), class = "sigma"),
          prior(normal(0, 0.1), class = "sd"))



#Implicit models - check of both priors
model_eb1.1_prior <- brm(overall_score ~ gender + (1|ID),
                    data = data_eb,
                    family = gaussian(),
                    prior = prior_eb1.1,
                    sample_prior = "only",
                    cores = 2,
                    seed = 123,
                    chains = 2)

model_eb1.2_prior <- brm(overall_score ~ gender + (1|ID),
                    data = data_eb,
                    family = gaussian(),
                    prior = prior_eb1.2,
                    sample_prior = "only",
                    seed = 123,
                    cores = 4,
                    chains = 4)

#prior check for both priors
pp_check(model_eb1.1_prior, nsamples = 100) #Doing a predictive prior check to test priors

pp_check(model_eb1.2_prior, nsamples = 100)

#models with both priors 
model_eb1.1 <- brm(overall_score ~ gender + (1|ID),
                   data = data_eb,
                   family = gaussian(),
                   prior = prior_eb1.1,
                   sample_prior = TRUE,
                   iter = 5000,
                   warmup = 2000,
                   cores = 4,
                   chains = 4,
                   seed = 123,
                   control = list(adapt_delta = 0.9))

model_eb1.2 <- brm(overall_score ~ gender + (1|ID),
                    data = data_eb,
                    family = gaussian(),
                    prior = prior_eb1.2,
                    sample_prior = TRUE,
                    iter = 5000,
                    warmup = 2000,
                    cores = 4,
                    chains = 4, 
                   seed = 123,
                    control = list(adapt_delta = 0.9)) 

waic(model_eb1.1, model_eb1.2)

summary(model_eb1.2)

marginal_effects(model_eb1.2)

summary(model_eb1.1)

marginal_effects(model_eb1.1)

plot(model_eb1.1)

#we will go with model eb1.1
```

##Benevolence predicted from gender and hostile score

```{r}
get_prior(benevolent_score ~ gender*hostile_score + (1|ID), data = data_eb)

#Defining a prior, mean set to 2.5 because best conceptual meaning
prior_eb2 = c(prior(normal(2.5, 0.5), class = "Intercept"), 
          prior(normal(0, 0.5), class = "b"), 
          prior(normal(0, 0.5), class = "sigma"),
          prior(normal(0, 0.1), class = "sd"))

model_eb2_prior <- brm(benevolent_score ~ gender*hostile_score + (1|ID),
                    data = data_eb,
                    family = gaussian(),
                    prior = prior_eb2,
                    sample_prior = "only",
                    cores = 2,
                    seed = 123,
                    chains = 2)

#prior check for both priors
pp_check(model_eb2_prior, nsamples = 100) #Doing a predictive prior check to test priors

#model
model_eb2 <- brm(benevolent_score ~ gender*hostile_score + (1|ID),
                 data = data_eb,
                 family = gaussian(),
                 prior = prior_eb2,
                 sample_prior = TRUE,
                 iter = 5000,
                 warmup = 2000,
                 cores = 4,
                 chains = 4, 
                 seed = 123,
                 control = list(adapt_delta = 0.9))

summary(model_eb2)

#Plotting
marginal_effects(model_eb2)

plot(model_eb2)
```


##Hostility predicted from gender and benevolent score

```{r}
get_prior(hostile_score ~ gender*benevolent_score + (1|ID), data = data_eb)

#Defining a prior, mean set to 2.5 because best conceptual meaning
prior_eb3 = c(prior(normal(2.5, 0.5), class = "Intercept"), 
          prior(normal(0, 0.5), class = "b"), 
          prior(normal(0, 0.5), class = "sigma"),
          prior(normal(0, 0.1), class = "sd"))

model_eb3_prior <- brm(hostile_score ~ gender*benevolent_score + (1|ID),
                    data = data_eb,
                    family = gaussian(),
                    prior = prior_eb3,
                    sample_prior = "only",
                    cores = 2,
                    seed = 123,
                    chains = 2)

#prior check for both priors
pp_check(model_eb3_prior, nsamples = 100) #Doing a predictive prior check to test priors

#model
model_eb3 <- brm(hostile_score ~ gender*benevolent_score + (1|ID),
                 data = data_eb,
                 family = gaussian(),
                 prior = prior_eb3,
                 sample_prior = TRUE,
                 iter = 5000,
                 warmup = 2000,
                 cores = 4,
                 chains = 4,
                 seed = 123,
                 control = list(adapt_delta = 0.9))

summary(model_eb3)

#Plotting
marginal_effects(model_eb3)

plot(model_eb3)
```

##Hypothesis testing
```{r}
#Model 1
#Females have higher overall sexism score than males
hypothesis(model_eb1.1, "genderMale = 0")


#Model 2
#Females and men have the same benevolent scores 
hypothesis(model_eb2, "0 = genderMale + genderMale:hostile_score")

hypothesis(model_eb2, "Intercept + hostile_score < Intercept + hostile_score + genderMale + genderMale:hostile_score")

#There is a positive relationship between benevolent score and hostile score across gender
hypothesis(model_eb2, "  0 < hostile_score + genderMale:hostile_score")


#Model 3
#females and males have the same hostile score
hypothesis(model_eb3, "0 = genderMale + genderMale:benevolent_score")

#females have a higher hostile score
hypothesis(model_eb3, "Intercept + benevolent_score > Intercept + benevolent_score + genderMale + genderMale:benevolent_score")

```

##Plotting explicit bias

###H3.1.1
```{r prepare predictions}
nd_eb1.1 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 10),
         ID = NA))

nd_eb1.1$gender <- ifelse(nd_eb1.1$gender == 0, "Male", "Female")

pred_eb1.1 <-
  predict(model_eb1.1, newdata = nd_eb1.1) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1)

pred_eb1.1_mean <- pred_eb1.1 %>% group_by(gender) %>% summarise(mean_prediction = mean(Estimate))
```


```{r H3.1.1 plot}
#create the plot
H3.1.1 <- ggplot(pred_eb1.1, aes(x = gender, y = overall_score, fill = gender)) +
  labs(x = "Gender", y = "Overall Sexism Score", title = "Hypothesis 3.1") +
  geom_boxplot(aes(x = gender, Estimate) , data = pred_eb1.1, width = 0.5, alpha = 0.4) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_point(aes(x = gender, y = mean_prediction), data = pred_eb1.1_mean, size = 2) + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(text = element_text(size=20)) + 
  ylim(low=1.45, high=1.85)

H3.1.1
```

###H3.2.1
```{r prepare predictions}
nd_eb1.1_2 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 10),
         ID = NA, 
         hostile_score = NA))

nd_eb1.1_2$gender <- ifelse(nd_eb1.1_2$gender == 0, "Male", "Female")

#Inserting mean hostile score for the different gender
nd_eb1.1_2$hostile_score[nd_eb1.1_2$gender== "Male"] <- data_eb %>% filter(gender=="Male")%>% summarise(hostile_score = as.numeric(mean(hostile_score)))

nd_eb1.1_2$hostile_score[nd_eb1.1_2$gender== "Female"] <- data_eb %>% filter(gender=="Female")%>% summarise(hostile_score = as.numeric(mean(hostile_score)))

#Changing hostile score to numeric
nd_eb1.1_2$hostile_score <- as.numeric(nd_eb1.1_2$hostile_score)

pred_eb1.1_2 <-
  predict(model_eb2, newdata = nd_eb1.1_2) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1_2)

pred_eb1.1_2_mean <- pred_eb1.1_2 %>% group_by(gender) %>% summarise(mean_prediction = mean(Estimate))
```


```{r H3.2.1 plot}
#create the plot
H3.2.1 <- ggplot(data_eb, aes(x = gender, y = benevolent_score, fill = gender)) +
  labs(x = "Gender", y = "Benevolent Score", title = "Hypothesis 3.2") +
  geom_boxplot(aes(x = gender, Estimate) , data = pred_eb1.1_2, width = 0.5, alpha = 0.4) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_point(aes(x = gender, y = mean_prediction), data = pred_eb1.1_2_mean, size = 2) + 
  scale_fill_manual(values=c("orange", "blue"))+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size=20)) + 
  ylim(low=1.45, high=1.85)
H3.2.1
```


###H3.2.2
```{r prepare predictions}
nd_eb1.1_3 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 3),
         ID = NA, 
         hostile_score = 0:5))

nd_eb1.1_3$gender <- ifelse(nd_eb1.1_3$gender == 0, "Male", "Female")

pred_eb1.1_3 <-
  predict(model_eb2, newdata = nd_eb1.1_3) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1_3)

```


```{r H3.2.1 plot}
#create the plot
H3.2.2 <- ggplot(data_eb, aes(x = hostile_score, y = benevolent_score)) +
  labs(x = "Hostile Score", y = "Benevolent Score", title = "Hypothesis 3.2") +
  geom_point(aes(x = hostile_score, benevolent_score, color = gender) , data = data_eb) + 
  geom_smooth(aes(x = hostile_score, y = Estimate, color = gender), data = pred_eb1.1_3) + 
    scale_color_manual(values=c("orange", "blue"))+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size=20))

H3.2.2$labels$colour <- "Gender"

H3.2.2
```

###H3.2.3
```{r prepare predictions}
nd_eb1.1_4 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 3),
         ID = NA, 
         hostile_score = 0:5))

nd_eb1.1_4$gender <- ifelse(nd_eb1.1_4$gender == 0, "Male", "Female")


pred_eb1.1_4 <-
  predict(model_eb2, newdata = nd_eb1.1_4) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1_4)

```


```{r H3.2.3 plot}
#create the plot
H3.2.3 <- ggplot(data_eb, aes(x = hostile_score, y = benevolent_score)) +
  labs(x = "Hostile Score", y = "Benevolent Score", title = "Hypothesis 3.2.3") +
  geom_point(aes(x = hostile_score, benevolent_score) , data = data_eb) + 
  geom_smooth(aes(x = hostile_score, y = Estimate), data = pred_eb1.1_4) + 
    scale_color_manual(values=c("orange", "blue"))+
  theme(plot.title = element_text(hjust = 0.5)) 

H3.2.3$labels$colour <- "Gender"

H3.2.3
```

###H3.3.1
```{r prepare predictions}
nd_eb1.1_5 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 10),
         ID = NA, 
         benevolent_score = NA))

nd_eb1.1_5$gender <- ifelse(nd_eb1.1_5$gender == 0, "Male", "Female")

#Inserting mean hostile score for the different gender
nd_eb1.1_5$benevolent_score[nd_eb1.1_2$gender== "Male"] <- data_eb %>% filter(gender=="Male")%>% summarise(benevolent_score = as.numeric(mean(benevolent_score)))

nd_eb1.1_5$benevolent_score[nd_eb1.1_2$gender== "Female"] <- data_eb %>% filter(gender=="Female")%>% summarise(benevolent_score = as.numeric(mean(benevolent_score)))

#Changing hostile score to numeric
nd_eb1.1_5$benevolent_score <- as.numeric(nd_eb1.1_5$benevolent_score)

pred_eb1.1_5 <-
  predict(model_eb3, newdata = nd_eb1.1_5) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1_5)

pred_eb1.1_5_mean <- pred_eb1.1_5 %>% group_by(gender) %>% summarise(mean_prediction = mean(Estimate))
```


```{r H3.3.1 plot}
#create the plot
H3.3.1 <- ggplot(data_eb, aes(x = gender, y = hostile_score, fill = gender)) +
  labs(x = "Gender", y = "Hostile Score", title = "Hypothesis 3.3") +
  geom_point(aes(x = gender, hostile_score) , data = data_eb, width = 0.5, alpha = 0.4) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_boxplot(aes(x = gender, y = Estimate), data = pred_eb1.1_5, size = 2) + 
  scale_fill_manual(values=c("orange", "blue"))+
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(text = element_text(size=20)) + 
  ylim(low=0, high=3)
H3.3.1
```


###H3.3.2
```{r prepare predictions}
nd_eb1.1_6 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 3),
         ID = NA, 
         benevolent_score = 0:5))

nd_eb1.1_6$gender <- ifelse(nd_eb1.1_6$gender == 0, "Male", "Female")

pred_eb1.1_6 <-
  predict(model_eb3, newdata = nd_eb1.1_6) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1_6)

```


```{r H3.3.2 plot}
#create the plot
H3.3.2 <- ggplot(data_eb, aes(x = benevolent_score, y = hostile_score)) +
  labs(x = "Benevolent Score", y = "Hostile Score", title = "Hypothesis 3.3.2") +
  geom_point(aes(x = benevolent_score, hostile_score, color = gender) , data = data_eb) + 
  geom_smooth(aes(x = benevolent_score, y = Estimate, color = gender), data = pred_eb1.1_6) + 
    scale_color_manual(values=c("orange", "blue"))+
  theme(plot.title = element_text(hjust = 0.5)) 

H3.3.2$labels$colour <- "Gender"

H3.3.2
```

###H3.3.3
```{r prepare predictions}
nd_eb1.1_7 <- expand.grid(tibble(
         gender=factor(0:1) %>% 
           rep(., times = 3),
         ID = NA, 
         benevolent_score = 0:5))

nd_eb1.1_7$gender <- ifelse(nd_eb1.1_7$gender == 0, "Male", "Female")


pred_eb1.1_7 <-
  predict(model_eb3, newdata = nd_eb1.1_7) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd_eb1.1_7)

```


```{r H3.3.3 plot}
#create the plot
H3.3.3 <- ggplot(data_eb, aes(x = benevolent_score, y = hostile_score)) +
  labs(x = "Benevolent Score", y = "Hostile Score", title = "Hypothesis 3.3.3") +
  geom_point(aes(x = benevolent_score, hostile_score) , data = data_eb) + 
  geom_smooth(aes(x = benevolent_score, y = Estimate), data = pred_eb1.1_7) + 
    scale_color_manual(values=c("orange", "blue"))+
  theme(plot.title = element_text(hjust = 0.5)) 

H3.3.3$labels$colour <- "Gender"

H3.3.3
```

###Arranging all plots in one
```{r}
grid.arrange(H3.1.1, H3.2.1, H3.3.1, nrow = 1)
```



#DECISION BIAS
Below are models: Firstly, the reconstructon of the model and the results from last year. Secondly, new combinations of the variables with the goal of finding the best model. 

###Analysis from last year (excluding skill difference)

```{r model excluding skill dif, replication of effects from last year, 1}

#Defining priors
prior_db1 <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_db1_prior <- brm(leader_behavior ~ 0 + Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_db1, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_db1_prior, nsamples = 100)


model_db1 <- brm(
  leader_behavior ~ 0 + Leader_gender : Follower_gender + ( 0 + skill_dif_roll_c : Follower_gender | SubjectID),
  data = data_db,
  prior = prior_db1,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 
summary(model_db1)

plot(model_db1)

marginal_effects(model_db1)
```

##New models
```{r full model, 2}
#Defining priors 
prior_db2 <- c( 
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_db2_prior <- brm(leader_behavior ~ 0 + conf_dif_c*skill_dif_roll_c*Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_db2, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_db2_prior, nsamples = 100)


model_db2 <- brm(leader_behavior ~ 0 + conf_dif_c*skill_dif_roll_c*Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID),
  data = data_db,
  prior = prior_db2,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 
marginal_effects(model_db2)

summary(model_db2) 

plot(model_db2)
```


```{r model for extracting decision bias per ID}
model_db2_ID <- brm(leader_behavior ~ 1 + Follower_gender + (conf_dif_c+skill_dif_roll_c):Follower_gender + (1 + Follower_gender + (conf_dif_c+skill_dif_roll_c):Follower_gender | SubjectID),
  data = data_db,
  prior = prior_db2,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 
```



```{r model without confidence, 3}
#Defining priors
prior_db3 <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_db3_prior <- brm(leader_behavior ~ 0 + skill_dif_roll_c*Leader_gender:Follower_gender+ (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_db3, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_db3_prior, nsamples = 100)


model_db3 <- brm(leader_behavior ~ 0 +skill_dif_roll_c*Leader_gender:Follower_gender+ (0 + skill_dif_roll_c:Follower_gender | SubjectID),
  data = data_db,
  prior = prior_db3,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 
summary(model_db3)
```

```{r model without skill difference, 4}
#Defining priors
prior_db4 <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_db4_prior <- brm(leader_behavior ~ 0 + conf_dif_c*Leader_gender:Follower_gender+ (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_db4, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       seed = 123,
                       chains = 2, 
                       cores = 2)

pp_check(model_db4_prior, nsamples = 100)


model_db4 <- brm(leader_behavior ~ 0 +conf_dif_c*Leader_gender:Follower_gender+ (0 + skill_dif_roll_c:Follower_gender | SubjectID),
  data = data_db,
  prior = prior_db4,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 
summary(model_db4)
```



##Investigating confidence variable
```{r}
#add column with absolute response
data_db_all$Response_abs <- abs(data_db_all$Response)

get_prior(Response_abs ~ Gender*Partner_gender + (1 | SubjectID), family = "gaussian",
                       data = data_db_all)
#Defining priors 
prior_db5 <- c( 
  prior(normal(2,1),class="Intercept"),
  prior(normal(0,.5),class="b"),
   prior(normal(0, .1),class="sd")
)

#prior predictive check
model_db5_prior <- brm(Response_abs ~ Gender*Partner_gender+ (1 | SubjectID), 
                       prior = prior_db5, 
                       data = data_db_all, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "gaussian", 
                       seed = 123,
                       chains = 2, 
                       cores = 2)

pp_check(model_db5_prior, nsamples = 100)


model_db5 <- brm(Response_abs ~ Gender*Partner_gender + (1 | SubjectID),
  data = data_db_all,
  prior = prior_db5,
  sample_prior=T,
  family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=6,
  cores=4,
  control = list(adapt_delta = 0.9999) 
) 
marginal_effects(model_db5)

plot(model_db5)
summary(model_db5)

```

##Investigating skill difference in relation to gender
```{r is men better than women regression, include = FALSE}

#Defining priors
prior_db6 <- c(
  prior(normal(0, 0.2),class="Intercept"),
  prior(normal(0,0.1),class="b"),
  prior(normal(0,0.2), class= "sd")
)


#prior predictive check
model_db6_prior <- brm(response_dummy ~ diff*Gender + (1+diff|SubjectID), 
                       prior = prior_db6, 
                       data = data_db_all, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2,
                       control= list(adapt_delta = 0.99),
                       seed = 123,
                       cores = 2)

pp_check(model_db6_prior, nsamples = 100)

# Model answer predicted by gender and difficulty
model_db6 <- brm(
  response_dummy ~ diff*Gender + (1+diff|SubjectID), 
  data = data_db_all,
  prior = prior_db6,
  family = "bernoulli",
  sample_prior=T,
  seed = 123, # Adding a seed makes results reproducible.
  cores=4,
  chains=4
) 
plot(model_db6)

summary(model_db6)

marginal_effects(model_db6)
```

##Waic
```{r waic}
waic <- waic(model_db1, model_db2)

waic

```

## Hypothesis testing


##H1.1.1Are men better than women? 
```{r}
#model db6 with star
hypothesis(model_db6, "diff < (diff+diff:GenderMale)")

```


##H1.5.2 Are females more discriminative towards their partner gender in terms of confidence?
```{r}
#model db5 
hypothesis(model_db5, "Partner_genderMale = (GenderMale + GenderMale:Partner_genderMale)")


hypothesis(model_db5, "(Intercept - (Intercept + Partner_genderMale)) > ((Intercept + GenderMale) -  (Intercept + GenderMale:Partner_genderMale))")


```

##H1.5.1 Males generally express higher confidence than females

```{r}
#model db5
hypothesis(model_db5, "((Intercept + (Intercept + Partner_genderMale)) / 2) < (((Intercept + GenderMale) + (Intercept + GenderMale:Partner_genderMale))/2)")
```

##H1.1.4; Males exploit the information given by the confidence of their partner more than females, when making a final decision
```{r}
#testing this hypothsis with model_db2
hypothesis(model_db2, "((conf_dif_c:Leader_genderFemale:Follower_genderFemale + conf_dif_c:Leader_genderFemale:Follower_genderMale)/2) = ( (conf_dif_c:Leader_genderMale:Follower_genderFemale + conf_dif_c:Leader_genderMale:Follower_genderMale)/2) ")

hypothesis(model_db2, "((conf_dif_c:Leader_genderFemale:Follower_genderFemale + conf_dif_c:Leader_genderFemale:Follower_genderMale)/2) > ( (conf_dif_c:Leader_genderMale:Follower_genderFemale + conf_dif_c:Leader_genderMale:Follower_genderMale)/2) ")

```

##H1.1.5; Females are more discriminative to their follower's gender in terms of the degree to which they exploit the information given by their partner's confidence than males
```{r}
hypothesis(model_db2, "(conf_dif_c:Leader_genderFemale:Follower_genderMale - conf_dif_c:Leader_genderFemale:Follower_genderFemale) = ( conf_dif_c:Leader_genderMale:Follower_genderMale - conf_dif_c:Leader_genderMale:Follower_genderFemale) ")


hypothesis(model_db2, "(conf_dif_c:Leader_genderFemale:Follower_genderMale - conf_dif_c:Leader_genderFemale:Follower_genderFemale) > ( conf_dif_c:Leader_genderMale:Follower_genderMale - conf_dif_c:Leader_genderMale:Follower_genderFemale) ")


```


##Bruges ikke: Males exploit the information given by the skill of their partner more than females, when making a final decision
```{r}
#testing this hypothsis with model_db2
hypothesis(model_db2, "((skill_dif_c:Leader_genderFemale:Follower_genderFemale + skill_dif_c:Leader_genderFemale:Follower_genderMale)/2) > ( (skill_dif_c:Leader_genderMale:Follower_genderFemale + skill_dif_c:Leader_genderMale:Follower_genderMale)/2) ")

```

##Bruges ikke: Females are more discriminative to their follower's gender in terms of the degree to which they exploit the information given by their partner's skill than males
```{r}

hypothesis(model_db2, "(skill_dif_c:Leader_genderFemale:Follower_genderMale - skill_dif_c:Leader_genderFemale:Follower_genderFemale) < ( skill_dif_c:Leader_genderMale:Follower_genderMale - skill_dif_c:Leader_genderMale:Follower_genderFemale) ")


```



###For the simple model (excluding skill difference and confidence difference)
H1: there is a leader effect: male leaders tend to surrender less than female leaders
```{r H1: there is a leader effect: male leaders tend to surrender less than female leaders}
#H1: In general male leader tend to surrender less than female leaders

hypothesis(model_db1, "(Leader_genderMale:Follower_genderMale + Leader_genderMale:Follower_genderFemale)/2 < (Leader_genderFemale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2")

```

H2: there is a follower effect: leaders tend to surrender more to men than to women
```{r H2: there is a follower effect: leaders tend to surrender more to men than to women }

# H2: There is a follower effect: leaders tend to surrender more to men than to women
hypothesis(model_db1, "(Leader_genderMale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2 > (Leader_genderMale:Follower_genderFemale + Leader_genderFemale:Follower_genderFemale)/2")


```

H3: There is an interaction: Females are more discriminative as to their followers gender than males are
```{r H3: there is an interaction, females are more discriminative as to their followers gender than males are }

hypothesis(model_db1, "(Leader_genderMale:Follower_genderMale - Leader_genderMale:Follower_genderFemale) < (Leader_genderFemale:Follower_genderMale - Leader_genderFemale:Follower_genderFemale)")


```


###For the complex model
```{r}
#H1.1: Leaders are less prone to surrender as a product of higher confidence difference i.e. the more higher confidence the leader has and lower confidence the follower has the less prone the leader is to surrender

hypothesis(model_db2, "conf_dif < 0")

#H1.2: Leaders are less prone to surrender as a product of higher skill difference i.e. the more higher skill the leader has and lower skill the follower has the less prone the leader is to surrender

hypothesis(model_db2, "skill_dif < 0")

#H1.3 In general male leader tend to surrender less than female leaders

hypothesis(model_db2, "(Leader_genderMale:Follower_genderMale + Leader_genderMale:Follower_genderFemale)/2 < (Leader_genderFemale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2")

#H1.4 There is a follower effect: leaders tend to surrender more to men than to women

hypothesis(model_db2, "(Leader_genderMale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2 > (Leader_genderMale:Follower_genderFemale + Leader_genderFemale:Follower_genderFemale)/2")

#H3: There is an interaction: males are more discriminative as to their followers gender than females are

hypothesis(model_db2, "(Leader_genderMale:Follower_genderMale - Leader_genderMale:Follower_genderFemale) < (Leader_genderFemale:Follower_genderMale - Leader_genderFemale:Follower_genderFemale)")

```



#Plotting

##Old model

Model_db1
Leader behavior ~ 0 + Leader gender:Follower gender + (0 + skill difference : Follower gender | Subject)


```{r}
nd_db1 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 6),
         Leader_gender = factor(0:1) %>% rep(., times = 6),
         skill_dif_roll_c = 0,
         SubjectID = NA))

nd_db1$Follower_gender <- ifelse(nd_db1$Follower_gender == 0, "Male", "Female")

nd_db1$Leader_gender <- ifelse(nd_db1$Leader_gender == 0, "Male", "Female")


pred_db1 <-
  predict(model_db1, newdata = nd_db1) %>%
  as_tibble() %>%
  bind_cols(nd_db1)

```


###H1.1.1: In general, male leaders tend to surrender less than female leaders.

```{r}
#create the plot
H1.1.1 <- ggplot(data_db, aes(x = Leader_gender, y = leader_behavior, fill = Leader_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "H1.1.1") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred_db1, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_db1, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db1$Estimate), max(pred_db1$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5))+ 
  theme(text = element_text(size=20))


H1.1.1

```

###H1.1.2: Leaders tend to surrender more to male followers than to female followers

```{r}
H1.1.2 <- ggplot(data_db, aes(x = Follower_gender, y = leader_behavior, fill = Follower_gender)) +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "H1.1.2") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred_db1, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred_db1, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db1$Estimate), max(pred_db1$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5))+ 
  theme(text = element_text(size=20))

H1.1.2

```


###H1.1.3: Females are more discriminative towards their follower’s gender than males are, i.e. for female leaders, the gender of the follower makes a larger difference to their decision than it does for male leaders.

```{r}
H1.1.3 <- ggplot(pred_db1, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_db1, width = 0.7, alpha = 0.6) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db1$Estimate), max(pred_db1$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1.1.1, 1.1.2 and 1.1.3 for model 1.1") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_y_continuous(labels = percent_format(accuracy = 2)) + 
  theme(text = element_text(size=20))


H1.1.3

```


##Full model

model_db2 <- brm(leader_behavior ~ 1 + Follower_gender + conf_dif_c*skill_dif_roll_c*Leader_gender:Follower_gender + (1 + Follower_gender + skill_dif_roll_c:Follower_gender | SubjectID)



###Equal skill and confidence difference

```{r with equal skill dif and conf dif }
nd_db2.1 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 3),
         Leader_gender = factor(0:1) %>% rep(., times = 3),
         conf_dif_c = c(0) %>% rep(., times = 6),
         skill_dif_roll_c = c(0) %>% rep(., times = 6),
         SubjectID = NA))


nd_db2.1$Follower_gender <- ifelse(nd_db2.1$Follower_gender == 0, "Male", "Female")

nd_db2.1$Leader_gender <- ifelse(nd_db2.1$Leader_gender == 0, "Male", "Female")


pred_db2.1 <-
  predict(model_db2, newdata = nd_db2.1) %>%
  as_tibble() %>%
  bind_cols(nd_db2.1)
```


####Test of H1, H2 and H3 on the full model

```{r}

H2.1.1 <- ggplot(data_db, aes(x = Leader_gender, y = leader_behavior, fill = Leader_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "H2.1.1") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred_db2.1, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_db2.1, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db2.1$Estimate), max(pred_db2.1$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("orange", "blue"))  + 
  theme(text = element_text(size=20))

H2.1.1



H2.1.2 <- ggplot(data_db, aes(x = Follower_gender, y = leader_behavior, fill = Follower_gender)) +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "H2.1.2") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred_db2.1, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred_db2.1, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db2.1$Estimate), max(pred_db2.1$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("orange", "blue"))  + 
  theme(text = element_text(size=20))

H2.1.2

H2.1.3 <- ggplot(pred_db2.1, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_db2.1, width = 0.7, alpha = 0.6) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db2.1$Estimate), max(pred_db2.1$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1.1.1, 1.1.2 and 1.1.3 for model 1.2 ") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5))  + 
  theme(text = element_text(size=20)) +
  scale_y_continuous(labels = percent_format(accuracy = 2)) 

H2.1.3
```


###Different confidence 

```{r with different confidence}
nd_db2 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 5),
         Leader_gender = factor(0:1) %>% rep(., times = 5),
         conf_dif_c = c((4/1-1), (4/2-1),(4/3-1), (3/1-1), (3/2-1),0, (3/4-1), (2/3-1), (2/4-1), (1/3-1)) %>% rep(., times = 1),
         skill_dif_roll_c = 0,
         SubjectID = NA))


nd_db2$Follower_gender <- ifelse(nd_db2$Follower_gender == 0, "Male", "Female")

nd_db2$Leader_gender <- ifelse(nd_db2$Leader_gender == 0, "Male", "Female")


pred_db2 <-
  predict(model_db2, newdata = nd_db2) %>%
  as_tibble() %>%
  bind_cols(nd_db2)

pred_db2_save <- pred_db2
```

####plot with different confidence
```{r}
#turn into factor
pred_db2$conf_dif_c <- as.character(pred_db2$conf_dif_c)
pred_db2$conf_dif_c <- as.factor(pred_db2$conf_dif_c)

#change order of factor levels
pred_db2$conf_dif_c <- factor(pred_db2$conf_dif_c,levels(pred_db2$conf_dif_c)[c(4,3,2,1,5,6,7,8,9,10)])

#change names of factor levels
levels(pred_db2$conf_dif_c) <- c("-0.67","-0.5","-0.33","-0.25","0","0.33","0.5", "1", "2", "3")

pred_db2$leader_follower <- NA
pred_db2$leader_follower[pred_db2$Leader_gender == "Female"  & pred_db2$Follower_gender == "Female"] <- "FF"
pred_db2$leader_follower[pred_db2$Leader_gender == "Female"  & pred_db2$Follower_gender == "Male"] <- "FM"
pred_db2$leader_follower[pred_db2$Leader_gender == "Male"  & pred_db2$Follower_gender == "Female"] <- "MF"
pred_db2$leader_follower[pred_db2$Leader_gender == "Male"  & pred_db2$Follower_gender == "Male"] <- "MM"


plot_conf <- ggplot(data=pred_db2, aes(x=conf_dif_c, y=Estimate, group=leader_follower))+
    geom_line(size=1, aes(color=leader_follower))+
    ylab("Predicted propensity to surrender")+
    xlab("Difference in confidence between leader and follower gender")+
    ggtitle("Difference in confidence and gender as predictors of propensity to surrender")+
    theme_bw()+
    scale_fill_manual(values=c("orange", "blue", "orange", "blue")) +
    theme(text = element_text(size=12),
        legend.text = element_text(size=12),
        legend.direction = "horizontal",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position="top")+ 
  theme(text = element_text(size=20))+labs(colour="Leader Gender, Follower Gender") +
  scale_y_continuous(labels = percent_format(accuracy = 2)) 


plot_conf
```


###Different skill


```{r}
nd_db2.2 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 3),
         Leader_gender = factor(0:1) %>% rep(., times = 3),
         conf_dif_c = 0,
         skill_dif_roll_c = seq(quantile(data_db$skill_dif_roll_c,probs=c(.025)), quantile(data_db$skill_dif_roll_c,probs=c(.975)), 0.1),
         SubjectID = NA))


nd_db2.2$Follower_gender <- ifelse(nd_db2.2$Follower_gender == 0, "Male", "Female")

nd_db2.2$Leader_gender <- ifelse(nd_db2.2$Leader_gender == 0, "Male", "Female")


pred_db2.2 <-
  predict(model_db2, newdata = nd_db2.2) %>%
  as_tibble() %>%
  bind_cols(nd_db2.2)


pred_db2.2_save <- pred_db2.2


```

####plot with different skill

```{r}
pred_db2.2$leader_follower <- NA
pred_db2.2$leader_follower[pred_db2.2$Leader_gender == "Female"  & pred_db2.2$Follower_gender == "Female"] <- "FF"
pred_db2.2$leader_follower[pred_db2.2$Leader_gender == "Female"  & pred_db2.2$Follower_gender == "Male"] <- "FM"
pred_db2.2$leader_follower[pred_db2.2$Leader_gender == "Male"  & pred_db2.2$Follower_gender == "Female"] <- "MF"
pred_db2.2$leader_follower[pred_db2.2$Leader_gender == "Male"  & pred_db2.2$Follower_gender == "Male"] <- "MM"


plot_skill <- ggplot(data=pred_db2.2, aes(x=skill_dif_roll_c, y=Estimate, group=leader_follower))+
    geom_point(size=1, aes(color=leader_follower))+
    ylab("Predicted propensity to surrender")+
    xlab("Difference in confidence between leader and follower gender")+
    ggtitle("Difference in confidence and gender as predictors of propensity to surrender")+
    theme_bw()+
    theme(text = element_text(size=12),
        legend.text = element_text(size=12),
        legend.direction = "horizontal",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position="top")

plot_skill
```


##Expressing confidence

Response absolute ~ Gender*Partner’s gender + (1 | Subject)

```{r}
nd_db3 <- expand.grid(tibble(
         Gender=factor(0:1) %>% rep(., times = 2),
         Partner_gender = factor(0:1) %>% rep(., times = 2),
         Response_abs = c(1,2,3,4),
         SubjectID = NA))


nd_db3$Gender <- ifelse(nd_db3$Gender == 0, "Male", "Female")

nd_db3$Partner_gender <- ifelse(nd_db3$Partner_gender == 0, "Male", "Female")


pred_db3 <-
  predict(model_db5, newdata = nd_db3) %>%
  as_tibble() %>%
  bind_cols(nd_db3)
```

```{r}
scaleFUN <- function(x) sprintf("%.2f", x)
H3 <- ggplot(pred_db3, aes(x = Gender, y = Estimate, fill = Partner_gender)) + 
  geom_violin(aes(x = Gender, y = Estimate), data = pred_db3, width = 0.7, alpha = 0.6) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db3$Estimate), max(pred_db3$Estimate), length.out=6), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Gender", y = "Mean expressed confidence", title = "Hypothesis 1.5.1 and 1.5.2") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Partner gender") + 
  scale_fill_manual(values=c("orange", "blue")) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(text = element_text(size=20)) +
  scale_y_continuous(labels=scaleFUN)


H3
```


Model_db1
Leader behavior ~ 0 + Leader gender:Follower gender + (0 + skill difference : Follower gender | Subject)


```{r}
nd_db1 <- expand.grid(tibble(
         Follower_gender=factor(0:2) %>% rep(., times = 10),
         Leader_gender = factor(0:2) %>% rep(., times = 10),
         SubjectID = NA))



nd_db1$Follower_gender <- ifelse(nd_db1$Follower_gender == 0, "Male", "Female")

nd_db1$Leader_gender <- ifelse(nd_db1$Leader_gender == 0, "Male", "Female")


pred_db1 <-
  predict(model_db1, newdata = nd_db1) %>%
  as_tibble() %>%
  bind_cols(nd_db1)

```


#H1.1.1: In general, male leaders tend to surrender less than female leaders.

```{r}
#create the plot
H1.1.1 <- ggplot(data_db, aes(x = Leader_gender, y = leader_behavior, fill = Leader_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "H1.1.1") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred_db1, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_db1, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db1$Estimate), max(pred_db1$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("orange", "blue"))

H1.1.1

```

#H1.1.2: Leaders tend to surrender more to male followers than to female followers

```{r}
H1.1.2 <- ggplot(data_db, aes(x = Follower_gender, y = leader_behavior, fill = Follower_gender)) +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "H1.1.2") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred_db1, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred_db1, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db1$Estimate), max(pred_db1$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("orange", "blue"))

H1.1.2

```


#H1.1.3: Females are more discriminative towards their follower’s gender than males are, i.e. for female leaders, the gender of the follower makes a larger difference to their decision than it does for male leaders.

```{r}
H1.1.3 <- ggplot(pred_db1, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_db1, width = 0.7, alpha = 0.8) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_db1$Estimate), max(pred_db1$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "H1.1.3") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("orange", "blue"))

H1.1.3

```





##Look into confidence variable 

```{r}
conf_plot <- ggplot(data_db, aes(x=Leader_gender, y=conf_dif_c, fill = Follower_gender)) + geom_boxplot() + facet_wrap(~Leader_gender)
conf_plot


plot1 <- ggplot(data_db, aes(x=conf_dif_c, y = leader_behavior, fill = Leader_gender)) + geom_point() + facet_wrap(~Leader_gender)
plot1


```

```{r prepare predictions}
nd <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 10),
         Leader_gender = factor(0:1) %>% rep(., times = 10),
         conf_dif = factor((4/1-1), (4/2-1),(4/3-1), 0, (3/1-1), (3/2-1), (3/4-1), (2/3-1), (2/4-1), (1/3-1), (1/4-1)) %>% rep(., times = 10),
         SubjectID = NA))

nd <- expand.grid(tibble(
         Follower_gender=seq(0:2) %>% rep(., times = 10),
         Leader_gender = factor(0:2) %>% rep(., times = 10),
         SubjectID = NA))



nd$Follower_gender <- ifelse(nd$Follower_gender == 0, "Male", "Female")

nd$Leader_gender <- ifelse(nd$Leader_gender == 0, "Male", "Female")


pred <-
  predict(model_db1, newdata = nd, re_formula = ~ (0 + Follower_gender | SubjectID)) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd)
```


```{r H1 plot}
#create the plot
H1 <- ggplot(disagree_db_long, aes(x = Leader_gender, y = leader_behavior, fill = Leader_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2"))
H1
```


```{r H2: plotting}

#create the plot
H2 <- ggplot(disagree_db_long, aes(x = Follower_gender, y = leader_behavior, fill = Follower_gender)) +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "Hypothesis 2") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2"))

H2
```

H3: plotting
```{r H3.1 plotting}
marginal_effects(model_db1)

#create the plot
H3.1 <- ggplot(disagree_db_long, aes(x = Leader_gender, y = leader_behavior, fill = Follower_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 3 - Boxplot") +
  geom_boxplot(aes(x = Leader_gender, Estimate, fill = Follower_gender) , data = pred, width = 0.5, alpha = 0.8) + 
  labs(fill = "Follower gender") +
  theme(panel.grid.minor = element_blank()) +
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5)))) +
  scale_fill_manual(values=c("palegreen3", "gold2"))

H3.1

```

```{r H3.2 Plotting}
H3.2 <- ggplot(pred, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, width = 0.7, alpha = 0.8) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 3") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("palegreen3", "gold2"))
```
 
 
##Model looking at confidence in relation to skill

```{r}

#create response abs
data_db_long$Response_abs <- abs(data_db_long$Response)
data_db_long$Response_abs_z <- scale(data_db_long$Response)


#remove the first 10 trials

data_db_long <- data_db_long[11:12352,]

#Defining priors 
prior_db_conf_skill <- c( 
  prior(normal(0,0.1),class="Intercept"),
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_db_conf_skill_prior <- brm(Sensitivity_roll ~ 1 + Response_abs_z * Gender + (1 | SubjectID), 
                       prior = prior_db_conf_skill, 
                       data = data_db_long, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "gaussian", 
                       chains = 2, 
                       cores = 2)

pp_check(model_db_conf_skill_prior, nsamples = 100)


model_db_conf_skill <- brm(Sensitivity_roll ~ 1 + Response_abs_z * Gender + (1 | SubjectID),
  data = data_db_long,
  prior = prior_db_conf_skill,
  sample_prior=T,
  family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4,
  control = list(adapt_delta = 0.9) 
) 

```

```{r extra shit from thea to all of us }

thea <- data_db_all

thea <- filter(data_db, Follower_gender != Leader_gender)




```

