---
title: "Models"
author: "MM"
date: "13/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r loading libraries}
pacman::p_load(
  lme4, 
  lmerTest, 
  brms, 
  tidyverse, 
  here,
  stringi, 
  tm, 
  ggrepel, 
  ggbeeswarm, 
  boot)

```

#Loading sensitivity scores (wide)
```{r load data}
#read csv files with estimates
data <- read.csv(
  here("Gender_bias_study_1", "data",
       "data_disagree_long_sensitivity.csv"))[,3:17] %>%
  mutate(
    Follower_gender = as.factor(Follower_gender),
    Leader_gender = as.factor(Leader_gender)
  )
data_long <- read.csv(here("Gender_bias_study_1", "data",
       "data_long_sensitivity.csv"))[,2:16]

```


##Model without skill difference (basic)

```{r model without skill difference}
# Defining formula
basic_m <- bf(
  leader_behaviour ~ 0 + Leader_gender : Follower_gender + 
    (0 + Follower_gender + Follower_gender:skill_dif_c | Subject))

#Defining priors
prior_basic <- c(
  prior(normal(0,.5),class="b"),
  prior(normal(0,1),class="sd")
)

#prior predictive check
prior_check_basic <- brm(
  basic_m, 
  prior = prior_basic, 
  data = data, 
  sample_prior = "only",
  iter = 4000, 
  family = "bernoulli", 
  chains = 2, 
  cores = 2)

pp_check(prior_check_basic, nsamples = 100)

#model without skill difference
m_basic <- brm(
  basic_m,
  data = data,
  prior = prior_basic,
  sample_prior = T,
  family = "bernoulli", 
  seed = 123, # Adding a seed makes results reproducible.
  chains = 2,
  cores = 2,
  iter = 4000,
  backend = "cmdstanr",
  threads = threading(2),
  control = list(
    adapt_delta = 0.99) 
) 

## Prior posterior update checks
Posterior <- posterior_samples(m_basic)

ggplot(Posterior) + theme_classic() +
  geom_density(aes(prior_b), fill="darkred",alpha=0.3) +
  geom_density(aes(`b_Leader_gender0:Follower_gender0`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender1:Follower_gender0`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender0:Follower_gender1`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender1:Follower_gender1`), fill="darkblue",alpha=0.3)

ggplot(Posterior) + theme_classic() +
  geom_density(aes(prior_sd_Subject), fill="darkred",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender0`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender1`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender0:skill_dif_c`), fill="darkgreen",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender1:skill_dif_c`), fill="darkgreen",alpha=0.3) 

# Model summary and plots
summary(m_basic)
plot(m_basic)
marginal_effects(m_basic)

```


##The full model with skill difference (full)
```{r, eval = FALSE}
#Get priors
full_f <- bf(
  leader_behaviour ~ 0 + Leader_gender:Follower_gender +
    Leader_gender:Follower_gender:skill_dif_c + 
    (0 + Follower_gender + Follower_gender:skill_dif_c | Subject ))

get_prior(full_f, data = data, family = "bernoulli")

#Defining priors
prior_full <- c(
  prior(normal(0,1),class="b"),
  prior(normal(0,.5),class="b", coef="Leader_gender0:Follower_gender0"),
  prior(normal(0,.5),class="b", coef="Leader_gender0:Follower_gender1"),
  prior(normal(0,.5),class="b", coef="Leader_gender1:Follower_gender0"),
  prior(normal(0,.5),class="b", coef="Leader_gender1:Follower_gender1"),
  prior(normal(0,1),class="sd")
)

#prior predictive check
prior_check_full <- brm(
  full_f,  
  data = data, 
  prior = prior_full,
  sample_prior = "only",
  iter = 4000, 
  family = "bernoulli", 
  chains = 2, 
  cores = 2
  backend = "cmdstanr",
  threads = threading(2),
  control = list(
    adapt_delta = 0.99
  ))

pp_check(prior_check_full, nsamples = 100)

# Model w skill difference
m_full <- brm(
  full_f,  
  data = data, 
  prior = prior_full,
  sample_prior = TRUE,
  iter = 4000, 
  family = "bernoulli", 
  chains = 2, 
  cores = 2,
  backend = "cmdstanr",
  threads = threading(2),
  control = list(
    adapt_delta = 0.99
  ))

## Prior posterior update checks
Posterior <- posterior_samples(m_full)

ggplot(Posterior) + theme_classic() +
  geom_density(aes(`prior_b_Leader_gender0:Follower_gender0`), fill="darkred",alpha=0.3) +
  geom_density(aes(`b_Leader_gender0:Follower_gender0`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender1:Follower_gender0`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender0:Follower_gender1`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender1:Follower_gender1`), fill="darkblue",alpha=0.3)

ggplot(Posterior) + theme_classic() +
  geom_density(aes(`prior_b_Leader_gender0:Follower_gender0:skill_dif_c`), fill="darkred",alpha=0.3) +
  geom_density(aes(`b_Leader_gender0:Follower_gender0:skill_dif_c`), fill="darkgreen",alpha=0.3) +
  geom_density(aes(`b_Leader_gender1:Follower_gender0:skill_dif_c`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender0:Follower_gender1:skill_dif_c`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`b_Leader_gender1:Follower_gender1:skill_dif_c`), fill="darkblue",alpha=0.3)

ggplot(Posterior) + theme_classic() +
  geom_density(aes(prior_sd_Subject), fill="darkred",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender0`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender1`), fill="darkblue",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender0:skill_dif_c`), fill="darkgreen",alpha=0.3) +
  geom_density(aes(`sd_Subject__Follower_gender1:skill_dif_c`), fill="darkgreen",alpha=0.3) 

summary(m_full)
plot(m_full)
conditional_effects(m_full)
```


#Model comparison

```{r, eval = FALSE}

m_basic <- add_criterion(m_basic, criterion = "loo")
m_full <- add_criterion(m_full, criterion = "loo")
loo_compare(m_full, m_basic)
loo_model_weights(m_full, m_basic)

```

#Hypothesis testing: H1a and H1b

# H1a: There is a leader effect: male leaders tend to surrender less than female leaders
```{r H1}

#H1a: In general male leaders tend to surrender less than female leaders
hypothesis(m_full, #m_basic
           "(Leader_gender0:Follower_gender0 + Leader_gender0:Follower_gender1)/2 < 
           (Leader_gender1:Follower_gender0 + Leader_gender1:Follower_gender1)/2")
hypothesis(m_full, #m_basic
           "(inv_logit(Leader_gender0:Follower_gender0) +
           inv_logit(Leader_gender0:Follower_gender1))/2*100 < 
           (inv_logit(Leader_gender1:Follower_gender0) +
           inv_logit(Leader_gender1:Follower_gender1))/2*100")

Posterior <- Posterior %>%
  mutate(
    Man2Man = inv_logit_scaled(`b_Leader_gender0:Follower_gender0`), 
    Man2Woman = inv_logit_scaled(`b_Leader_gender0:Follower_gender1`),
    Woman2Man = inv_logit_scaled(`b_Leader_gender1:Follower_gender0`),
    Woman2Woman = inv_logit_scaled(`b_Leader_gender1:Follower_gender1`),
    ManLeader = (Man2Man + Man2Woman)/2,
    WomanLeader = (Woman2Man + Woman2Woman)/2,
    ManFollower = (Man2Man + Woman2Man)/2,
    WomanFollower = (Man2Woman + Woman2Woman)/2,
    H1a = ManLeader - WomanLeader,
    H1b = ManFollower - WomanFollower,
    Man2ManBetter = inv_logit_scaled(`b_Leader_gender0:Follower_gender0` + `b_Leader_gender0:Follower_gender0:skill_dif_c`), 
    Man2ManWorse = inv_logit_scaled(`b_Leader_gender0:Follower_gender0` - `b_Leader_gender0:Follower_gender0:skill_dif_c`),  
    Man2WomanBetter = inv_logit_scaled(`b_Leader_gender0:Follower_gender1` + `b_Leader_gender0:Follower_gender0:skill_dif_c`), 
    Man2WomanWorse = inv_logit_scaled(`b_Leader_gender0:Follower_gender1` - `b_Leader_gender0:Follower_gender0:skill_dif_c`),  
    Woman2ManBetter = inv_logit_scaled(`b_Leader_gender1:Follower_gender0` + `b_Leader_gender0:Follower_gender0:skill_dif_c`), 
    Woman2ManWorse = inv_logit_scaled(`b_Leader_gender1:Follower_gender0` - `b_Leader_gender0:Follower_gender0:skill_dif_c`),  
    Woman2WomanBetter = inv_logit_scaled(`b_Leader_gender1:Follower_gender1` + `b_Leader_gender0:Follower_gender0:skill_dif_c`), 
    Woman2WomanWorse = inv_logit_scaled(`b_Leader_gender1:Follower_gender1` - `b_Leader_gender0:Follower_gender0:skill_dif_c`),
    ManLeaderBetter = (Man2ManBetter + Man2WomanBetter)/2,
    WomanLeaderBetter = (Woman2ManBetter + Woman2WomanBetter)/2,
    ManFollowerBetter = (Man2ManBetter + Woman2ManBetter)/2,
    WomanFollowerBetter = (Man2WomanBetter + Woman2WomanBetter)/2,
    H1aBetter = ManLeaderBetter - WomanLeaderBetter,
    H1bBetter = ManFollowerBetter - WomanFollowerBetter,
    ManLeaderWorse = (Man2ManWorse + Man2WomanWorse)/2,
    WomanLeaderWorse = (Woman2ManWorse + Woman2WomanWorse)/2,
    ManFollowerWorse = (Man2ManWorse + Woman2ManWorse)/2,
    WomanFollowerWorse = (Man2WomanWorse + Woman2WomanWorse)/2,
    H1aWorse = ManLeaderWorse - WomanLeaderWorse,
    H1bWorse = ManFollowerWorse - WomanFollowerWorse
  )
mean(Posterior$ManLeader)
mean(Posterior$WomanLeader)
mean(Posterior$H1a)
quantile(Posterior$H1a, c(0.025, 0.975))
sum(Posterior$H1a<0)/sum(!(Posterior$H1a<0))

mean(Posterior$H1aBetter)
sum(Posterior$H1aBetter<0)/sum(!(Posterior$H1aBetter<0))
mean(Posterior$H1aWorse)
sum(Posterior$H1aWorse<0)/sum(!(Posterior$H1aWorse<0))


```

## H1a: Plotting
```{r preparing predictions}
#create newdata to make predictions from 
nd <- 
  expand.grid(tibble(
         Follower_gender = factor(0:1) %>% rep(., times = 10),
         Leader_gender = factor(0:1) %>% rep(., times = 10),
         skill_dif_c = 0,
         Subject = NA))

#Predicting new values from the basic model
pred <-
  predict(m_full, newdata = nd) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd)

#Changing the format of the follower and leader gender
pred$Leader_gender <- as.character(pred$Leader_gender)
pred$Follower_gender <- as.character(pred$Follower_gender)

#Changing the genders from dummy coding
pred$Follower_gender[pred$Follower_gender == 0] <- "Male"
pred$Follower_gender[pred$Follower_gender == 1] <- "Female"
pred$Leader_gender[pred$Leader_gender == 0] <- "Male"
pred$Leader_gender[pred$Leader_gender == 1] <- "Female"
```

```{r H1 plot}
#Creating a rounding function for plots
rounding <- function(x) sprintf("%.3f", x)

#create the plot
H1a <- ggplot(data, aes(x = Leader_gender, y = leader_behaviour, fill = Leader_gender)) +
  theme_classic() +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1a") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate,fill = Leader_gender), data = pred, trim = FALSE, width =1, alpha = 0.2) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5)), labels = rounding) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2")) +
  theme(plot.title = element_text(hjust = 0.5))

H1a
```


#H1b:There is a follower effect: leaders tend to surrender more to men than to women
```{r H1b: there is a follower effect: leaders tend to surrender more to men than to women }
# H2: There is a follower effect: leaders tend to surrender more to men than to women
hypothesis(m_full, "(Leader_gender0:Follower_gender0 + Leader_gender1:Follower_gender0)/2 > (Leader_gender0:Follower_gender1 + Leader_gender1:Follower_gender1)/2")
mean(Posterior$ManFollower)
mean(Posterior$WomanFollower)
mean(Posterior$H1b)
quantile(Posterior$H1b, c(0.025, 0.975))
sum(Posterior$H1b>0)/sum(!(Posterior$H1b>0))
mean(Posterior$H1bBetter)
mean(Posterior$H1bWorse)

#testing the effect of inv.logit before hyp
hypothesis(m_full, "(inv.logit(Leader_gender0:Follower_gender0) + inv.logit(Leader_gender1:Follower_gender0))/2*100 > (inv.logit(Leader_gender0:Follower_gender1) + inv.logit(Leader_gender1:Follower_gender1))/2*100")

hypothesis(m_full, "(inv.logit(Leader_gender0:Follower_gender0) - inv.logit(Leader_gender0:Follower_gender1)) > (inv.logit(Leader_gender1:Follower_gender0) - inv.logit(Leader_gender1:Follower_gender1))")
```

##H1b: Plotting
```{r}
#create the plot
H1b <- ggplot(data, aes(x = Follower_gender, y = leader_behaviour, fill = Follower_gender)) +
  theme_classic() +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "Hypothesis 1b") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.2) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5)), labels = rounding) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2"))+
  theme(plot.title = element_text(hjust = 0.5))

H1b
```


##both hypotheses visualized
```{r}
main_plot <- ggplot(pred, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  theme_classic() +
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, width = 0.7, alpha = 0.8) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5)), labels = rounding) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Gender bias") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("palegreen3", "gold2"))+
  theme(plot.title = element_text(hjust = 0.5))

main_plot

```


#Alternative hypothesis: Are men better than women?
##Modelling: Are men better than women?
```{r}
#Defining priors
prior_mf <- c(
  prior(normal(0, 0.2),class="Intercept"),
  prior(normal(0,0.1),class="b"),
  prior(normal(0,0.1), class= "sd", coef = "dif_blue", group = "Subject"),
  prior(normal(0,0.2), class= "sd", coef = "Intercept", group = "Subject")
)


#prior predictive check
prior_check_mf <- brm(answer ~ dif_blue*Gender + (1+dif_blue|Subject), prior = prior_mf, data = data_long, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_mf, nsamples = 100)

# Model testing skill difference
skill_mf <- brm(
  answer ~ dif_blue*Gender + (1+dif_blue|Subject), 
  data = data_long,
  prior = prior_mf,
  family = "bernoulli",
  sample_prior=T,
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2
) 


summary(skill_mf)
plot(skill_mf)
marginal_effects(skill_mf)

```

##Hypothesis testing: Men perform better than women
```{r}
#Men perform better than women
hypothesis(skill_mf, "dif_blue < (dif_blue+dif_blue:GenderMale)")

hypothesis(skill_mf, "dif_blue > (dif_blue+dif_blue:GenderMale)")

hypothesis(skill_mf, "dif_blue = (dif_blue+dif_blue:GenderMale)")

#No

```







