---
title: "Preprocessing"
author: "MM"
date: "2/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading packages
```{r loading packages, include = FALSE}
pacman::p_load(
  brms,
  tidyverse,
  here,
  tidybayes,
  LaplacesDemon,
  tidyr,
  reshape2)

```

#Loading and processing data 
```{r}

data <- read.csv(
  here("Gender_bias_study_1", "data", "anonymised_data.csv")) %>%
  mutate(
    # Making unique subjects
    unique_ID_right = paste(GroupNumber, SubjectID_right, sep = "_"),
    unique_ID_left = paste(GroupNumber, SubjectID_left, sep = "_"),
    # Calculating evidence
    dif_blue  = Prop_blue_image_2 - Prop_blue_image_1,
    # Calculating difficulty
    dif_blue_abs = abs(Prop_blue_image_2 - Prop_blue_image_1),
    # Calculating joint answers
    joint_answer = Joint_right + Joint_left,
    # Fix some stuff
    joint_answer = ifelse(joint_answer == 0, NA, ifelse(joint_answer == -1, 0, joint_answer))
  ) %>%  rename(
    right_answer = Response_right,
    left_answer = Response_left
  )
```


##Adding variables: Agree, chosen leader and gender
```{r coding for leader/follower}

data <- data %>%
  mutate(
    # variable that sorts out all the agreed trials
    chosen_leader = ifelse(right_answer == left_answer, "Agree", 0),
    # variable, which determines the chosen leader
    chosen_leader = ifelse(chosen_leader == 0 & Joint_right == 0, 
                           "Left_lead",
                           ifelse(chosen_leader == 0 & Joint_left == 0,
                                  "Right_lead",
                                  chosen_leader)),
    #create column that specifies the gender of the leader
    Leader_gender = ifelse(chosen_leader == "Left_lead",
                           as.character(Gender_left),
                           ifelse(chosen_leader == "Right_lead",
                                  as.character(Gender_right),
                                  NA)),
    Leader_gender = ifelse(Leader_gender == "Male", 0,
                           ifelse(Leader_gender =="Female", 1, NA)),
    #create column that specifies the gender of the follower
    Follower_gender = ifelse(chosen_leader == "Left_lead",
                           as.character(Gender_right),
                           ifelse(chosen_leader == "Right_lead",
                                  as.character(Gender_left),
                                  NA)),
    Follower_gender = ifelse(Follower_gender == "Male", 0,
                           ifelse(Follower_gender =="Female", 1, NA)),
  )
```

##Adding variable: Leader behaviour

```{r Did the leader stick?}
#Creating column of 0's
data$leader_behaviour <- 0 

#Inserting cases were leader stick for right leader
data$leader_behaviour[data$chosen_leader == "Right_lead" & data$joint_answer == data$right_answer] <- "stick" 

#Inserting cases were leader surrender for right leader
data$leader_behaviour[data$chosen_leader == "Right_lead" & data$joint_answer != data$right_answer] <- "surrender" 

#Inserting cases were leader stick for left leader
data$leader_behaviour[data$chosen_leader == "Left_lead" & data$joint_answer == data$left_answer] <- "stick" 

#Inserting cases were leader surreder for left leader
data$leader_behaviour[data$chosen_leader == "Left_lead" & data$joint_answer != data$left_answer] <- "surrender" 

#Removing cases were they agree
data$leader_behaviour[data$chosen_leader == "Agree"] <- NA 

#dummycode leader behaviour , surrender = 1, stick = 0
data$leader_behaviour[data$leader_behaviour == "surrender"] <- 1

data$leader_behaviour[data$leader_behaviour == "stick"] <- 0

```


```{r adding trial variable to dataset in wide format}
#Creating a trial variable
n = 1
p = NULL
data_j = NULL
 for (p in unique(data$GroupNumber)){
   if (n == 1) {
     data_j <- filter(data, data$GroupNumber == p)
     data_j <- cbind(data_j, as.data.frame(1:sum(complete.cases(data_j$GroupNumber))))
     print(sum(complete.cases(data_j$GroupNumber)))
     colnames(data_j)[44] <- "Trial"
     n = n + 1
     } else {
     data_j <- rbind(data_j,mutate(filter(data, data$GroupNumber == p), Trial = 1:sum(complete.cases(filter(data, data$GroupNumber == p)$GroupNumber))))
     print(sum(complete.cases(filter(data, data$GroupNumber == p)$GroupNumber)))
     n = n + 1
   }
 }

data = data_j

#remove extra trials (above 127) to have equal number of trials for all participants
data <- filter(data, data$Trial<=127)
```



#Sensitivity scores, partial pooling
We need one column containing answer from both left and right in order to allow pooling between all participants

##Long format
```{r making long format, include = FALSE}

#Subsetting the left data
left <- subset(data, select = c(GroupNumber, unique_ID_left, dif_blue, left_answer, joint_answer, Correct_left, Correct_joint, dif_blue_abs, Trial))

#Changing names
names(left) <- c("GroupNumber", "unique", "dif_blue", "answer", "joint_answer", "Correct", "Correct_joint", "dif_blue_abs", "Trial")

#Adding a side variable
left$Side <- "Left"

#Subsetting right data
right <- subset(data, select = c(GroupNumber, unique_ID_right, dif_blue, right_answer, joint_answer, Correct_left, Correct_joint, dif_blue_abs, Trial))

#Changing names
names(right) <- c("GroupNumber", "unique", "dif_blue", "answer", "joint_answer", "Correct", "Correct_joint", "dif_blue_abs", "Trial")

#Adding a side variable
right$Side <- "Right"

#Removing half the joint data to inform the model, there is only one. 
right$Correct_joint <- NA
right$joint_answer <- NA

#Joining the dataframes
ldata <- rbind(left, right)

#Setting NA in correct answers
ldata$Correct_joint[is.na(ldata$joint_answer)] <- NA

```


##Modelling sensitivity scores with a rolling window
```{r rolling window sensitivity model, eval = FALSE}

#Making a number of iterations variable
n = 1
s = 1
t = 10
k = 0

## Defining the model
sensitivity_f <- bf(answer ~ 1 + dif_blue + (1 + dif_blue | unique))
### Defining priors
prior_sensitivity =  c(
      prior(normal(0,0.2), class = "Intercept"),
      prior(normal(0,0.1), class = "b", coef = "dif_blue"),
      prior(normal(0,0.1), class = "sd", coef = "dif_blue", group = "unique"),
      prior(normal(0,0.2), class = "sd", coef = "Intercept", group = "unique")
    )

###Making a loop for individual slope
for (i in unique(ldata$Trial)){ #Loop through number of trials, 127 because it is the biggest amount of trials 
  print(i)
  if(i == 10){ #If the first 10
    for (p in unique(ldata$unique)){
      if (n == 1) {
        data_i <- filter(ldata, ldata$unique == p)[s:t, ]
        n = n + 1
      } else {
        data_i <- rbind(data_i, filter(ldata, ldata$unique == p)[s:t, ])
        n = n + 1
      } }
    
    #Making the model - using answer
    m_sensitivity <- brm(
      sensitivity_f,
      data = data_i,
      prior = prior_sensitivity,
      family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
      seed = 123,# Adding a seed makes results reproducible.
      cores = 2,
      chains = 2,
      #control = list(adapt_delta = 0.9)
    )
    
    ###SAVING ESTIMATES
    #Saving random effect for individual slope
    sensitivity_scores_roll <- as.data.frame(ranef(m_sensitivity))[,5] + fixef(m_sensitivity)[2,1]
    
    #Adding rownames
    sensitivity_scores_roll <- cbind(Row.Names = rownames(as.data.frame(ranef(m_sensitivity))[,5:6]), as.data.frame(sensitivity_scores_roll))
    
    colnames(sensitivity_scores_roll) <- c("unique", i)
  }
  
  if(i > 10){
    k = k + 1
    n = 1
    s = s + 1
    t = t + 1
    for (r in unique(ldata$unique)){
      if (n == 1) {
        data_i <- filter(ldata, ldata$unique == r)[s:t, ]
        n = n + 1
      } else {
        data_i <- rbind(data_i, filter(ldata, ldata$unique == r)[s:t, ])
        n = n + 1
      } }
    
    #Making the model - using answer
    m_sensitivity <- brm(
      sensitivity_f,
      data = data_i,
      prior = prior_sensitivity,
      family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
      seed = 123,# Adding a seed makes results reproducible.
      cores = 2,
      chains = 2,
      #control = list(adapt_delta = 0.9)
    )
    
    ###SAVING ESTIMATES
    
    #Saving random effect for individual slope
    sensitivity_scores_roll_temp <- as.data.frame(ranef(m_sensitivity))[,5] + fixef(m_sensitivity)[2,1]
    
    #Cbind new results to sensitivity score
    sensitivity_scores_roll <- cbind(sensitivity_scores_roll, sensitivity_scores_roll_temp)
    
    colnames(sensitivity_scores_roll)[k+2] <- i
    
  } 
}
```

#Write a csv-file with the sensitivity scores
```{r write and read csv, eval = FALSE}
  
#write.csv(sensitivity_scores_roll, file = here("Gender_bias_Study_1","data","sensitivity_scores_rolling.csv"))

#Loading the sensitivity scores again?
sensitivity_scores_roll <- read.csv(
  here("Gender_bias_Study_1","data","sensitivity_scores_rolling.csv"))
```

#Merge the sensitivity scores with the existing data frame
```{r merge the new results with the long data frame}

#Reshaping the data
mdata <- melt(sensitivity_scores_roll, id.vars=c("unique"), measure.vars = c(colnames(sensitivity_scores_roll)[3:120]), variable.name = "Trial", value.name = "Sensitivity_roll")

#Remove useless X in trial column
mdata$Trial <-str_replace_all(mdata$Trial, "X", "")

#Merge ldata with sensitivity scores
sensitivity_scores <- merge(ldata, mdata, by = c("unique", "Trial"), all.x = TRUE, all.y = TRUE) #Insert NAs on trials lower than 10

```

#Transforming the data into wide format

```{r make wide to merge with disagree data}
#Subsetting to include only relevant columns
sensitivity_scores <- select(sensitivity_scores, 
                             -c("GroupNumber", "dif_blue","answer", 
                                "joint_answer", "Correct", "Correct_joint",
                                "dif_blue_abs"))

#Dividing into left and right data
sensitivity_scores_right <- filter(sensitivity_scores, Side == "Right")
sensitivity_scores_left <- filter(sensitivity_scores, Side == "Left")

#Deleting side column
sensitivity_scores_right <- subset(sensitivity_scores_right, select = -c(Side))
sensitivity_scores_left <- subset(sensitivity_scores_left, select = -c(Side))

#Renaming columns
colnames(sensitivity_scores_left) <-  c("unique_ID_left","Trial_left", "Sensitivity_roll_left")
colnames(sensitivity_scores_right) <-  c("unique_ID_right", "Trial_right",  "Sensitivity_roll_right")


#Creating a column for trial to the right
data$Trial_right <- data$Trial 

#Creating an identical column for trial to the left
colnames(data)[44] <- "Trial_left"

#Merging left data with sensitivity scores
data <- merge(data, sensitivity_scores_left, by = c("unique_ID_left", "Trial_left"))

#Merging right data with sensitivity scores
data <- merge(data, sensitivity_scores_right, by = c("unique_ID_right", "Trial_right"))


```


#Adding variable: Skill difference
```{r calculate skill difference}

data$skill_dif <- 0 #Creating column of 0


#Calculating skill difference
data$skill_dif <- ifelse(data$chosen_leader == "Left_lead", data$Sensitivity_roll_left/data$Sensitivity_roll_right, data$Sensitivity_roll_right/data$Sensitivity_roll_left) #calculating skill difference as a ratio between leader and follower sensitivity

#centering skill difference, so that a skill difference of 0 resembles equal skill
data$skill_dif_c <- 0
data$skill_dif_c <- (data$skill_dif)-1 

#Insert NAs in all agree trials
data$skill_dif[data$chosen_leader == "Agree"] <- NA 
data$skill_dif_c[data$chosen_leader == "Agree"] <- NA 

```

#Making long format

##Subsetting left data
```{r}
#Subset to left data
data_left <- subset(data, select = c(GroupNumber, unique_ID_left, dif_blue, dif_blue_abs, chosen_leader, Leader_gender, Follower_gender, skill_dif, skill_dif_c, leader_behaviour, Sensitivity_roll_left, Gender_left, left_answer, Trial_left)) #take all data for left participant

data_left$leader_behaviour[data_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
data_left$Leader_gender[data_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
data_left$Follower_gender[data_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
data_left$skill_dif[data_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
data_left$skill_dif_c[data_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left

```

##Subsetting right data
```{r}
#Subset right data
data_right <- subset(data, select = c(GroupNumber, unique_ID_right, dif_blue, dif_blue_abs, chosen_leader, Leader_gender, Follower_gender, skill_dif, skill_dif_c, leader_behaviour, Sensitivity_roll_right, Gender_right, right_answer, Trial_right)) #Subsetting right data

data_right$leader_behaviour[data_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

data_right$Leader_gender[data_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

data_right$Follower_gender[data_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

data_right$skill_dif[data_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

data_right$skill_dif_c[data_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right
```

##Merging data frames
```{r make long format}

#rename columns to not contain left or right
names(data_left) <- gsub(pattern = "_left", replacement = "", x = names(data_left))
names(data_left) <- gsub(pattern = "left_", replacement = "", x = names(data_left))
names(data_right) <- gsub(pattern = "_right", replacement = "", x = names(data_right))
names(data_right) <- gsub(pattern = "right_", replacement = "", x = names(data_right))


#Rbinding left and right data
data_long <- rbind(data_left, data_right)

```



```{r}
#remove the groupnumber from subject name to account for within participant variation
data_long$Subject <- as.character(data_long$unique_ID)

data_long$Subject <- gsub(".*_", "", data_long$Subject)
```


#Write CSV with sensitivity scores and clean data
```{r}
write.csv(data_long, file = 
            here("Gender_bias_Study_1","data", "data_long_sensitivity.csv")

data_long <- read.csv(
  here("Gender_bias_Study_1","data","data_long_sensitivity.csv")
```


#Removing agree-trials
```{r}
#Removing all agree trials
data_disagree_long <- na.omit(data_long)

```


#Cleaning the long data
```{r}
#remove the groupnumber from subject name to account for within participant variation
data_disagree_long$Subject <- as.character(data_disagree_long$unique_ID)

data_disagree_long$Subject <- gsub(".*_", "", data_disagree_long$Subject)

```


#Write CSV with sensitivity scores and clean data, only disagree
```{r}
write.csv(data_disagree_long, file = 
            here("Gender_bias_Study_1","data","data_disagree_long_sensitivity.csv")
```

