---
title: "Models"
author: "Thea Rolskov Sloth"
date: "15/10/2019"
output: html_document
---

#Getting packages
```{r loading packages, include = FALSE}
library(pacman)
p_load(brms, tidyverse, tidybayes, ggplot2, LaplacesDemon, rethinking, tidyr, reshape2, tibble, plotly, jpeg, tm, ggrepel, utils, boot, Hmisc, scales, gridExtra, pROC)
```

#Setting directory
```{r}
setwd("~/gender_bias_in_decision_making/Gender_bias_study_2") #Signe
setwd("C:/Users/KK/OneDrive - Aarhus Universitet/Dokumenter/MM, udgives/gender_bias_in_decision_making/Gender_bias_study_2") #Kiri
```


#Loading data
```{r}
data_db <- read.csv("disagree_sensitivity_GBDM_long_format.csv")[, 2:40] 
data_db_all <- read.csv("data_long_format_GBDM.csv")
```


#Models

##Model 1, same analysis as study 1 (excluding skill difference and confidence difference)
```{r model 1, excluding skill difference and confidence difference}

#Defining priors
prior_1 <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#Prior predictive check
model_1_prior <- brm(leader_behavior ~ 0 + Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_1, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_1_prior, nsamples = 100)


#Model 1
model_1 <- brm(
  leader_behavior ~ 0 + Leader_gender : Follower_gender + ( 0 + skill_dif_roll_c : Follower_gender | SubjectID),
  data = data_db,
  prior = prior_1,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 

#Model summary and plots
summary(model_1)
plot(model_1)
marginal_effects(model_1)
```


##Model 2 (including skill difference and confidence difference)
```{r model 2, including skill difference and confidence difference}
#Defining priors 
prior_2 <- c( 
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_2_prior <- brm(leader_behavior ~ 0 + conf_dif_c*skill_dif_roll_c*Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_2, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_2_prior, nsamples = 100)

#Model 2; including skill difference and confidence difference
model_2 <- brm(leader_behavior ~ 0 + conf_dif_c*skill_dif_roll_c*Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID),
  data = data_db,
  prior = prior_2,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 

#Model summary and plots
summary(model_2)
plot(model_2)
marginal_effects(model_2)

```



##Model 2.2 (including confidence difference)
```{r model 2, including confidence difference}
#Defining priors 
prior_2.2 <- c( 
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_2.2_prior <- brm(leader_behavior ~ 0 + conf_dif_c*Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_2, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_2.2_prior, nsamples = 100)

#Model 2; including skill difference and confidence difference
model_2.2 <- brm(leader_behavior ~ 0 + conf_dif_c*Leader_gender:Follower_gender + (0 + skill_dif_roll_c:Follower_gender | SubjectID),
  data = data_db,
  prior = prior_2.2,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 

#Model summary and plots
summary(model_2.2)
plot(model_2.2)
marginal_effects(model_2.2)

```





##Model 3, investigating skill difference in relation to gender 
```{r model 3, investigating difference in skill between genders}

#Defining priors
prior_3 <- c(
  prior(normal(0, 0.2),class="Intercept"),
  prior(normal(0,0.1),class="b"),
  prior(normal(0,0.2), class= "sd")
)


#prior predictive check
model_3_prior <- brm(response_dummy ~ diff*Gender + (1+diff|SubjectID), 
                       prior = prior_3, 
                       data = data_db_all, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2,
                       control= list(adapt_delta = 0.99),
                       seed = 123,
                       cores = 2)

pp_check(model_3_prior, nsamples = 100)

# Model 3
model_3 <- brm(
  response_dummy ~ diff*Gender + (1+diff|SubjectID), 
  data = data_db_all,
  prior = prior_3,
  family = "bernoulli",
  sample_prior=T,
  seed = 123, # Adding a seed makes results reproducible.
  cores=4,
  chains=4
) 

#Model summary and plots
summary(model_3)
plot(model_3)
marginal_effects(model_3)

```


##Model 4, investigating confidence variable in relation to gender
```{r model 4, investigating confidence variable in relation to gender }

#add column with absolute response
data_db_all$Response_abs <- abs(data_db_all$Response)

get_prior(Response_abs ~ Gender*Partner_gender + (1 | SubjectID), family = "gaussian",
                       data = data_db_all)
#Defining priors 
prior_4 <- c( 
  prior(normal(2,1),class="Intercept"),
  prior(normal(0,.5),class="b"),
   prior(normal(0, .1),class="sd")
)


#prior predictive check
model_4_prior <- brm(Response_abs ~ Gender*Partner_gender+ (1 | SubjectID), 
                       prior = prior_4, 
                       data = data_db_all, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "gaussian", 
                       seed = 123,
                       chains = 2, 
                       cores = 2)

pp_check(model_4_prior, nsamples = 100)

#Model 4
model_4 <- brm(Response_abs ~ Gender*Partner_gender + (1 | SubjectID),
  data = data_db_all,
  prior = prior_4,
  sample_prior=T,
  family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=6,
  cores=4,
  control = list(adapt_delta = 0.9999) 
) 

#Model summary and plots
summary(model_4)
plot(model_4)
marginal_effects(model_4)


```

##Model 5, confidence only

```{r Model 5, model only with confidence, for fun}

#Defining priors 
prior_5 <- c( 
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
model_5_prior <- brm(leader_behavior ~ 0 + conf_dif_c + (0 + skill_dif_roll_c:Follower_gender | SubjectID), 
                       prior = prior_5, 
                       data = data_db, 
                       sample_prior = "only",
                       iter = 4000, 
                       family = "bernoulli", 
                       chains = 2, 
                       cores = 2)

pp_check(model_5_prior, nsamples = 100)

#Model 5; only confience
model_5 <- brm(leader_behavior ~ 0 + conf_dif_c + (0 + skill_dif_roll_c:Follower_gender | SubjectID),
  data = data_db,
  prior = prior_5,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=4,
  cores=4
  #control = list(adapt_delta = 0.9) 
) 

#Model summary and plots
summary(model_5)
plot(model_5)
marginal_effects(model_5)

```




#WAIC testing
```{r WAIC testing to compare model 1 and model 2}
waic <- waic(model_1, model_2)

waic_2 <- waic(model_2, model_2.2)

waic

waic_2
```


#Hypothesis testing


##Hypothesis testing with model 1


###H1.1: There is an effect of leader in relation to gender: male leaders tend to surrender less than female leaders
```{r H1.1 of model_1}

#H1.1 of model_1
hypothesis(model_1, "(Leader_genderMale:Follower_genderMale + Leader_genderMale:Follower_genderFemale)/2 < (Leader_genderFemale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2")

```


###H1.2: There is an effect of follower in relation to gender: leaders tend to surrender more to men than to women
```{r H1.2 of model_1}

#H1.2 of model_1
hypothesis(model_1, "(Leader_genderMale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2 > (Leader_genderMale:Follower_genderFemale + Leader_genderFemale:Follower_genderFemale)/2")


```


##Hypothesis testing with model 2


###H2.1: There is an effect of leader in relation to gender: male leaders tend to surrender less than female leaders
```{r H2.1 of model_2}

#H2.1 of model_2
hypothesis(model_2, "(Leader_genderMale:Follower_genderMale + Leader_genderMale:Follower_genderFemale)/2 < (Leader_genderFemale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2")

```


###H2.2: There is an effect of follower in relation to gender: leaders tend to surrender more to men than to women
```{H2.2 of model_2}

#H2.2 of model_2
hypothesis(model_2, "(Leader_genderMale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2 > (Leader_genderMale:Follower_genderFemale + Leader_genderFemale:Follower_genderFemale)/2")

```

###H2.3: Males exploit the information given by the confidence of their partner more than females, when making a final decision
```{r}
#testing this hypothsis with model_db2
hypothesis(model_db2, "((conf_dif_c:Leader_genderFemale:Follower_genderFemale + conf_dif_c:Leader_genderFemale:Follower_genderMale)/2) > ( (conf_dif_c:Leader_genderMale:Follower_genderFemale + conf_dif_c:Leader_genderMale:Follower_genderMale)/2) ")

```

###H2.4:Females are more discriminative to their follower's gender in terms of the degree to which they exploit the information given by their partner's confidence than males
```{r}

hypothesis(model_db2, "(conf_dif_c:Leader_genderFemale:Follower_genderMale - conf_dif_c:Leader_genderFemale:Follower_genderFemale) > ( conf_dif_c:Leader_genderMale:Follower_genderMale - conf_dif_c:Leader_genderMale:Follower_genderFemale) ")


```



##Hypothesis testing with model 2.2


###H2.1: There is an effect of leader in relation to gender: male leaders tend to surrender less than female leaders
```{r H2.1 of model_2}

#H2.1 of model_2
hypothesis(model_2.2, "(Leader_genderMale:Follower_genderMale + Leader_genderMale:Follower_genderFemale)/2 < (Leader_genderFemale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2")

```


###H2.2: There is an effect of follower in relation to gender: leaders tend to surrender more to men than to women
```{H2.2 of model_2}

#H2.2 of model_2
hypothesis(model_2.2, "(Leader_genderMale:Follower_genderMale + Leader_genderFemale:Follower_genderMale)/2 > (Leader_genderMale:Follower_genderFemale + Leader_genderFemale:Follower_genderFemale)/2")

```

###H2.3: Males exploit the information given by the confidence of their partner more than females, when making a final decision
```{r}
#testing this hypothsis with model_db2
hypothesis(model_2.2, "((conf_dif_c:Leader_genderFemale:Follower_genderFemale + conf_dif_c:Leader_genderFemale:Follower_genderMale)/2) > ( (conf_dif_c:Leader_genderMale:Follower_genderFemale + conf_dif_c:Leader_genderMale:Follower_genderMale)/2) ")

```

###H2.4:Females are more discriminative to their follower's gender in terms of the degree to which they exploit the information given by their partner's confidence than males
```{r}

hypothesis(model_2.2, "(conf_dif_c:Leader_genderFemale:Follower_genderMale - conf_dif_c:Leader_genderFemale:Follower_genderFemale) > ( conf_dif_c:Leader_genderMale:Follower_genderMale - conf_dif_c:Leader_genderMale:Follower_genderFemale) ")


```








##Hypothesis testing with model 3


###H3.1: Males and females perform equally well in the task
```{r H3.1 of model_3}
#H3.1 of model_3
hypothesis(model_3, "diff = (diff+diff:GenderMale)")

```


##Hypothesis testing with model 4


###H4.1: Males generally express higher confidence than females
```{r H4.1 of model_4}
#H4.1 of model_4
hypothesis(model_4, "((Intercept + (Intercept + Partner_genderMale)) / 2) < (((Intercept + GenderMale) + (Intercept + GenderMale:Partner_genderMale))/2)")
```


###H4.2: Females and males are equally affected by their partner's gender in terms of how they express their own confidence
```{r H4.2 of model_4}
#H4.2 of model_4
hypothesis(model_4, "Partner_genderMale = (GenderMale + GenderMale:Partner_genderMale)")


#testing alternative hypothesis with direction (females are more affected by their partner's gender in terms of how they express their own confidence)
hypothesis(model_4, "(Intercept - (Intercept + Partner_genderMale)) > ((Intercept + GenderMale) -  (Intercept + GenderMale:Partner_genderMale))")

#testing alternative hypothesis with direction (males are more affected by their partner's gender in terms of how they express their own confidence)
hypothesis(model_4, "(Intercept - (Intercept + Partner_genderMale)) < ((Intercept + GenderMale) -  (Intercept + GenderMale:Partner_genderMale))")

```


#Plotting the hypotheses

##Predictions from model 1
```{r create predictions from model 1}
nd_1 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 6),
         Leader_gender = factor(0:1) %>% rep(., times = 6),
         skill_dif_roll_c = 0,
         SubjectID = NA))

nd_1$Follower_gender <- ifelse(nd_1$Follower_gender == 0, "Male", "Female")

nd_1$Leader_gender <- ifelse(nd_1$Leader_gender == 0, "Male", "Female")


pred_1 <-
  predict(model_1, newdata = nd_1) %>%
  as_tibble() %>%
  bind_cols(nd_1)

```


###H1.1 og H1.2: 
```{r plot of H1.3}
H1.1_2 <- ggplot(pred_1, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_1, width = 0.7, alpha = 0.6) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_1$Estimate), max(pred_1$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1.1, 1.2 and 1.3 for model 1") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  scale_y_continuous(labels = percent_format(accuracy = 2)) + 
  theme(text = element_text(size=20))


H1.1_2

```


##Predictions from model 2 (equal skill difference and confidence difference)
```{r create predictions from model 2, with equal skill difference and confidence difference }
nd_2 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 3),
         Leader_gender = factor(0:1) %>% rep(., times = 3),
         conf_dif_c = c(0) %>% rep(., times = 6),
         skill_dif_roll_c = c(0) %>% rep(., times = 6),
         SubjectID = NA))


nd_2$Follower_gender <- ifelse(nd_2$Follower_gender == 0, "Male", "Female")

nd_2$Leader_gender <- ifelse(nd_2$Leader_gender == 0, "Male", "Female")


pred_2 <-
  predict(model_2, newdata = nd_2) %>%
  as_tibble() %>%
  bind_cols(nd_2)
```

###H2.1 og H2.2:
```{r plot of H2.3}
H2.1_2 <- ggplot(pred_2, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred_2, width = 0.7, alpha = 0.6) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_2$Estimate), max(pred_2$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 2.1, 2.2 and 2.3 for model 2 ") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("orange", "blue")) +
  theme(plot.title = element_text(hjust = 0.5))  + 
  theme(text = element_text(size=20)) +
  scale_y_continuous(labels = percent_format(accuracy = 2)) 

H2.1_2
```


##Predictions from model 2 (different confidence and equal skill difference) 
```{r create predictions from model 2, with different confidence and equal skill difference}
nd_2.0 <- expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 5),
         Leader_gender = factor(0:1) %>% rep(., times = 5),
         conf_dif_c = c((4/1-1), (4/2-1),(4/3-1), (3/1-1), (3/2-1),0, (3/4-1), (2/3-1), (2/4-1), (1/3-1)) %>% rep(., times = 1),
         skill_dif_roll_c = 0,
         SubjectID = NA))


nd_2.0$Follower_gender <- ifelse(nd_2.0$Follower_gender == 0, "Male", "Female")

nd_2.0$Leader_gender <- ifelse(nd_2.0$Leader_gender == 0, "Male", "Female")


pred_2.0 <-
  predict(model_2, newdata = nd_2.0) %>%
  as_tibble() %>%
  bind_cols(nd_2.0)

```

###Plot with difference in confidence between leader and follower and equal skill level
```{r plot with difference in confidence between leader and follower}
#turn into factor
pred_2.0$conf_dif_c <- as.character(pred_2.0$conf_dif_c)
pred_2.0$conf_dif_c <- as.factor(pred_2.0$conf_dif_c)

#change order of factor levels
pred_2.0$conf_dif_c <- factor(pred_2.0$conf_dif_c,levels(pred_2.0$conf_dif_c)[c(4,3,2,1,5,6,7,8,9,10)])

#change names of factor levels
levels(pred_2.0$conf_dif_c) <- c("-0.67","-0.5","-0.33","-0.25","0","0.33","0.5", "1", "2", "3")

pred_2.0$leader_follower <- NA
pred_2.0$leader_follower[pred_2.0$Leader_gender == "Female"  & pred_2.0$Follower_gender == "Female"] <- "FF"
pred_2.0$leader_follower[pred_2.0$Leader_gender == "Female"  & pred_2.0$Follower_gender == "Male"] <- "FM"
pred_2.0$leader_follower[pred_2.0$Leader_gender == "Male"  & pred_2.0$Follower_gender == "Female"] <- "MF"
pred_2.0$leader_follower[pred_2.0$Leader_gender == "Male"  & pred_2.0$Follower_gender == "Male"] <- "MM"


plot_conf <- ggplot(data=pred_2.0, aes(x=conf_dif_c, y=Estimate, group=leader_follower))+
    geom_line(size=1, aes(color=leader_follower))+
    ylab("Predicted propensity to surrender")+
    xlab("Difference in confidence between leader and follower gender")+
    ggtitle("Difference in confidence and gender as predictors of propensity to surrender")+
    theme_bw()+
    scale_fill_manual(values=c("orange", "blue", "orange", "blue")) +
    theme(text = element_text(size=12),
        legend.text = element_text(size=12),
        legend.direction = "horizontal",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position="top")+ 
  theme(text = element_text(size=20))+labs(colour="Leader Gender, Follower Gender") +
  scale_y_continuous(labels = percent_format(accuracy = 2)) 


plot_conf
```


##Predictions from model 4
```{r creating predictions from model 4}
nd_4 <- expand.grid(tibble(
         Gender=factor(0:1) %>% rep(., times = 2),
         Partner_gender = factor(0:1) %>% rep(., times = 2),
         Response_abs = c(1,2,3,4),
         SubjectID = NA))


nd_4$Gender <- ifelse(nd_4$Gender == 0, "Male", "Female")

nd_4$Partner_gender <- ifelse(nd_4$Partner_gender == 0, "Male", "Female")


pred_4 <-
  predict(model_4, newdata = nd_4) %>%
  as_tibble() %>%
  bind_cols(nd_4)
```


###H4.1: Males generally express higher confidence than females

###H4.2: Females and males are equally affected by their partner's gender in terms of how they express their own confidence
```{r plot of H4.1 and H4.2}
scaleFUN <- function(x) sprintf("%.2f", x)
H4 <- ggplot(pred_4, aes(x = Gender, y = Estimate, fill = Partner_gender)) + 
  geom_violin(aes(x = Gender, y = Estimate), data = pred_4, width = 0.7, alpha = 0.6) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred_4$Estimate), max(pred_4$Estimate), length.out=6), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Gender", y = "Mean expressed confidence", title = "Hypothesis 4.1 and 4.2") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Partner gender") + 
  scale_fill_manual(values=c("orange", "blue")) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(text = element_text(size=20)) +
  scale_y_continuous(labels=scaleFUN)


H4
```



#Confidence investigation
##Is there a correlation between confidence and accuracy? nd is it different for men and women? Baseret på artikel, Fleming & Lau (2014)
```{r}

#Make a variable of hard end easy trials
data_db_all$difficulty_level <- ifelse(data_db_all$diff <=5 & data_db_all$diff >=-5, "hard", "easy")

#Make a variable of high (1) and low confidence (0)
data_db_all$confidence_level <- ifelse(data_db_all$Response <=2 & data_db_all$Response >=-2, 0, 1) #Motivate threshold


#Make a confusion table of false and true positives and negatives
Correct = filter(data_db_all, difficulty_level =="easy")$Correct
Confidence = filter(data_db_all, difficulty_level =="easy")$confidence_level

table(Correct, Confidence)

#EASY TRIALS
#Across gender sensitivity, easy trials
roc1 <- roc(filter(data_db_all, difficulty_level =="easy")$Correct, filter(data_db_all, difficulty_level =="easy")$confidence_level)
plot(roc1, legacy.axes = TRUE, asp = 0)
auc(roc1) #finder arealet under kurven, bør være end 0.5

#Female sensitivity, easy trials
roc2 <- roc(filter(data_db_all, Gender =="Female" & difficulty_level =="easy")$Correct, filter(data_db_all, Gender =="Female" & difficulty_level =="easy")$confidence_level)
plot(roc2, legacy.axes = TRUE, asp = 0)
auc(roc2) #finder arealet under kurven, bør være højere end 0.5

#Male sensitivity, easy trials 
roc3 <- roc(filter(data_db_all, Gender =="Male" & difficulty_level =="easy")$Correct, filter(data_db_all, Gender =="Male" & difficulty_level =="easy")$confidence_level)
plot(roc3, legacy.axes = TRUE, asp = 0)
auc(roc3) #finder arealet under kurven, bør være højere end 0.5


#HARD TRIALS
#Across gender sensitivity, hard trials
roc4 <- roc(filter(data_db_all, difficulty_level =="hard")$Correct, filter(data_db_all, difficulty_level =="hard")$confidence_level)
plot(roc4, legacy.axes = TRUE, asp = 0)
auc(roc4) #finder arealet under kurven, bør være end 0.5

#Female sensitivity, hard trials
roc5 <- roc(filter(data_db_all, Gender =="Female" & difficulty_level =="hard")$Correct, filter(data_db_all, Gender =="Female" & difficulty_level =="hard")$confidence_level)
plot(roc5, legacy.axes = TRUE, asp = 0)
auc(roc5) #finder arealet under kurven, bør være højere end 0.5

#Male sensitivity, hard trials 
roc6 <- roc(filter(data_db_all, Gender =="Male" & difficulty_level =="hard")$Correct, filter(data_db_all, Gender =="Male" & difficulty_level =="hard")$confidence_level)
plot(roc6, legacy.axes = TRUE, asp = 0)
auc(roc6) #finder arealet under kurven, bør være højere end 0.5

```

Akserne i ROC-curve kan forklares således 
- Sensitivity: True positive rate: p(confidence | correct): "Hvis jeg svarer rigtigt, så svarer også at jeg er 100 % sikker"
-  1-Specificity (True negative rate): p(confidence | incorrect)
