---
title: "after_riccardo_analysis"
author: "Signe Kløve Kjær"
date: "13/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Preparing mark down
```{r setting working directory}
#set working directory 
setwd("~/gender_bias_in_decision_making/Gender_bias_study_1/") #Signe
#setwd("~/SocKultExam") #Thea
```

```{r loading libraries}
#load libraries
library(pacman)
p_load(lme4, lmerTest, brms, tidyverse, stringi, tm, ggrepel, ggbeeswarm)
```

##PREPARE POOLING DATA

```{r load data}
#read csv files with estimates
pool_estimates <- read.csv("pooling_individual_wide.csv")
```


```{r clean pooling data}

#Change names for sensitivity slopes
names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_answer_left'] <- 'Est_dif_blue_left_answer'

names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_answer_right'] <- 'Est_dif_blue_right_answer'

names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_correct_left'] <- 'Est_dif_blue_left_correct'

names(pool_estimates)[names(pool_estimates) == 'Slope_ranef_fixef_estimate_correct_right'] <- 'Est_dif_blue_right_correct'


#Create chosen-leader-column 
pool_estimates$chosen_leader <- ifelse(pool_estimates$right_answer == pool_estimates$left_answer, "Agree", 0) #create a column that sorts out all the agreed trials

#Create variable, which determines the chosen leader
pool_estimates$chosen_leader[pool_estimates$chosen_leader == 0 & pool_estimates$Joint_right == 0] <- "Left_lead"
pool_estimates$chosen_leader[pool_estimates$chosen_leader == 0 & pool_estimates$Joint_left == 0] <- "Right_lead"

#create column that specifies the gender of the leader
pool_estimates$Leader_gender <- 0
pool_estimates$Leader_gender <- ifelse(pool_estimates$chosen_leader == "Left_lead", as.character(pool_estimates$Gender_left), as.character(pool_estimates$Gender_right))
pool_estimates$Leader_gender[pool_estimates$chosen_leader == "Agree"] <- NA

#create column that specifies the gender of the follower
pool_estimates$Follower_gender <- 0
pool_estimates$Follower_gender <- ifelse(pool_estimates$chosen_leader == "Left_lead", as.character(pool_estimates$Gender_right), as.character(pool_estimates$Gender_left))
pool_estimates$Follower_gender[pool_estimates$chosen_leader == "Agree"] <- NA


#create stubborn leader
pool_estimates$Stubborn_leader <- 0 #Creating column of 0's

pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Right_lead" & pool_estimates$joint_answer == pool_estimates$right_answer] <- "stick" #Inserting cases were leader stick for right leader
pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Right_lead" & pool_estimates$joint_answer != pool_estimates$right_answer] <- "surrender" #Inserting cases were leader surrender for right leader

pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Left_lead" & pool_estimates$joint_answer == pool_estimates$left_answer] <- "stick" #Inserting cases were leader stick for left leader
pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Left_lead" & pool_estimates$joint_answer != pool_estimates$left_answer] <- "surrender" #Inserting cases were leader surreder for left leader

pool_estimates$Stubborn_leader[pool_estimates$chosen_leader == "Agree"] <- NA #Removing cases were they agree


#code leader and follower gender as dummies, 0 = male, 1 = female
pool_estimates$Leader_gender[pool_estimates$Leader_gender == "Male"] <- 0

pool_estimates$Leader_gender[pool_estimates$Leader_gender == "Female"] <- 1

pool_estimates$Follower_gender[pool_estimates$Follower_gender == "Male"] <- 0

pool_estimates$Follower_gender[pool_estimates$Follower_gender == "Female"] <- 1


#Rename stubborn-leader-column
names(pool_estimates)[names(pool_estimates) == 'Stubborn_leader'] <- 'Surrender'

pool_estimates$Surrender <- as.character(pool_estimates$Surrender)

#dummy code surrender columns, surrender = 1, stick = 0
pool_estimates$Surrender[pool_estimates$Surrender == "surrender"] <- 1

pool_estimates$Surrender[pool_estimates$Surrender == "stick"] <- 0

pool_estimates$Surrender[pool_estimates$chosen_leader == "Agree"] <- NA

#rename confidence
names(pool_estimates)[names(pool_estimates) == 'Response_left'] <- 'confidence_left'
names(pool_estimates)[names(pool_estimates) == 'Response_right'] <- 'confidence_right'

pool_data <- pool_estimates
```


```{r calculate skill difference}

#Calculating skill difference

#for answer
pool_estimates$skill_dif_answer <- 0 #Creating column of 0
pool_estimates$skill_dif_answer <- ifelse(pool_estimates$chosen_leader == "Left_lead", pool_estimates$Est_dif_blue_left_answer/pool_estimates$Est_dif_blue_right_answer, pool_estimates$Est_dif_blue_right_answer/pool_estimates$Est_dif_blue_left_answer) #calculating skill difference as a ratio between leader and follower sensitivity

pool_estimates$skill_dif_answer[pool_estimates$chosen_leader == "Agree"] <- NA #Insert NAs in all agree trials

#for correct
pool_estimates$skill_dif_correct <- 0 #Creating column of 0
pool_estimates$skill_dif_correct <- ifelse(pool_estimates$chosen_leader == "Left_lead", pool_estimates$Est_dif_blue_left_correct/pool_estimates$Est_dif_blue_right_correct, pool_estimates$Est_dif_blue_right_correct/pool_estimates$Est_dif_blue_left_correct) #calculating skill difference as a ratio between leader and follower sensitivity

pool_estimates$skill_dif_correct[pool_estimates$chosen_leader == "Agree"] <- NA #Insert NAs in all agree trials

```


```{r make long format}
#Subset to left data
pool_left <- subset(pool_estimates, select = c(GroupNumber, unique_ID_left, dif_blue, dif_blue_abs, chosen_leader, Leader_gender, Follower_gender, skill_dif_answer, confidence_left, Surrender, Est_dif_blue_left_answer, Gender_left, left_answer, Correct_left)) #take all data for left participant

pool_left$skill_dif_answer[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
pool_left$skill_dif_correct[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left

pool_left$Surrender[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
pool_left$Leader_gender[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left
pool_left$Follower_gender[pool_left$chosen_leader != 'Left_lead'] <- NA #insert NAs for chosen leader if not left

#Subset right data
pool_right <- subset(pool_estimates, select = c(GroupNumber, unique_ID_right, dif_blue, dif_blue_abs, chosen_leader, Leader_gender, Follower_gender, skill_dif_answer, confidence_right, Surrender, Est_dif_blue_right_answer, Gender_right, right_answer, Correct_right)) #Subsetting right data

pool_right$skill_dif_answer[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right
pool_right$skill_dif_correct[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

pool_right$Surrender[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

pool_right$Leader_gender[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

pool_right$Follower_gender[pool_right$chosen_leader != 'Right_lead'] <- NA #insert NAs for chosen leader if not right

#Renaming the columns to match
names(pool_left) <- c("GroupNumber", "unique_ID", "dif_blue", "dif_blue_abs", "chosen_leader", "Leader_gender", "Follower_gender", "skill_dif_answer", "confidence", "Surrender", "skill_level", "Gender", "answer", "correct")

names(pool_right) <- c("GroupNumber", "unique_ID", "dif_blue", "dif_blue_abs", "chosen_leader", "Leader_gender", "Follower_gender", "skill_dif_answer", "confidence", "Surrender", "skill_level", "Gender", "answer", "correct")

#Rbinding left and right data
pool_long <- rbind(pool_left, pool_right)
pool_long <- pool_long[1:14]


names(pool_long)[names(pool_long) == 'unique_ID'] <- 'Subject'

pool_long$Subject <- as.character(pool_long$Subject)
pool_long$Subject <- tolower(pool_long$Subject)

pool_long$Subject <- str_extract(pool_long$Subject,"[a-z]+")

#Removing all agree trials
pool_disagree <- na.omit(pool_long)

#Renaming unique_ID column
names(pool_disagree)[names(pool_disagree) == 'unique_ID'] <- 'Subject'

# #Removing outliers for the answer model
# pool_disagree_outlier_rem <- subset(pool_disagree, Subject != "14_signekirk")
# 
# pool_disagree_outlier_rem$Subject <- as.character(pool_disagree_outlier_rem$Subject)
# pool_disagree_outlier_rem$Subject <- tolower(pool_disagree_outlier_rem$Subject)
# 
# pool_disagree_outlier_rem$Subject <- str_extract(pool_disagree_outlier_rem$Subject,"[a-z]+")

#make confidence absolute 
#pool_long$Confidence <- abs(pool_long$Confidence)

#remove the groupnumber from subject name to account for within participant variation
pool_disagree$Subject <- as.character(pool_disagree$Subject)
pool_disagree$Subject <- tolower(pool_disagree$Subject)

pool_disagree$Subject <- str_extract(pool_disagree$Subject,"[a-z]+")

#scale the skill difference variable 
pool_disagree$skill_dif_answer <- scale(pool_disagree$skill_dif_answer)

```

#are men better than women?
```{r is men better than women regression, include = FALSE}

#Defining priors
prior_mf <- c(
  prior(normal(0, 0.2),class="Intercept"),
  prior(normal(0,0.1),class="b"),
  prior(normal(0,0.2), class= "sd", coef = "dif_blue", group = "Subject"),
  prior(normal(0,0.1), class= "sd", coef = "Intercept", group = "Subject")
)


# Model w skill difference
skill_mf <- brm(
  answer ~ dif_blue + dif_blue:Gender + (1+dif_blue|Subject), 
  data = pool_long,
  prior = prior_mf,
  family = "bernoulli",
  sample_prior=T,
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2
) 

summary(skill_mf)

prior_mf_correct <- c(
  prior(normal(0, 0.2),class="Intercept"),
  prior(normal(0,0.1),class="b")
  )


correct_mf <- brm(
  correct ~ Gender, 
  data = pool_long,
  prior = prior_mf_correct,
  family = "bernoulli",
  sample_prior=T,
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2
) 

summary(correct_mf)


male <- subset(pool_long, Gender == "Male")

female <- subset(pool_long, Gender == "Female")

table(male$correct)
table(female$correct)

```
 


#MODELS
```{r run the answer model with skill difference}
#Get priors
get_prior(Surrender ~ 0 + skill_dif_answer * Leader_gender * Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject ), data = pool_disagree, family = "bernoulli")

#Defining priors
prior_answer <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
prior_check_answer <- brm(Surrender ~ 0 + skill_dif_answer * Leader_gender * Follower_gender + (0 + skill_dif_answer:Follower_gender | Subject ), prior = prior_answer, data = pool_disagree, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_answer, nsamples = 100)

# Model w skill difference
m_answer <- brm(
  Surrender ~ 0 + skill_dif_answer * Leader_gender * Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject),
  data = pool_disagree,
  prior = prior_answer,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2,
  control = list(adapt_delta = 0.9) #only for answer model, due to Eff.Sample
) 

summary(m_answer)
```






```{r model without skill difference}
#Defining priors
prior_0 <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
prior_check_0 <- brm(Surrender ~ 0 + Leader_gender : Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject), prior = prior_0, data = pool_disagree, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_0, nsamples = 100)

#model without skill difference
m_0 <- brm(
  Surrender ~ 0 + Leader_gender : Follower_gender + (1 + skill_dif_answer:Follower_gender | Subject),
  data = pool_disagree,
  prior = prior_0,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=2,
  cores=2,
  control = list(adapt_delta = 0.9) 
) 


m_0.1 <- brm(
  Surrender ~ 0 + Leader_gender : Follower_gender + ( 0 + Follower_gender | Subject),
  data = pool_disagree,
  prior = prior_0,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=2,
  cores=2,
  control = list(adapt_delta = 0.9) 
) 

summary(m_0.1)
marginal_effects(m_0)

```



#MODEL COMPARISON

```{r answer and correct}
waic(m_answer, m_0)


summary(m_0)
```



#### #### #### #### #### #### HYPOTHESIS TESTING #### #### #### #### #### #### 



# H1: there is a leader effect: male leaders tend to surrender less than female leaders
```{r H1: there is a leader effect: male leaders tend to surrender less than female leaders}
#H1: In general male leader tend to surrender more than female leaders

hypothesis(m_0, "(Leader_gender0:Follower_gender0 + Leader_gender0:Follower_gender1)/2 < (Leader_gender1:Follower_gender0 + Leader_gender1:Follower_gender1)/2")



```

# H1: plotting
```{r prepare predictions}

#create newdata to make predictions from 
nd <- 
  expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 10),
         Leader_gender = factor(0:1) %>% rep(., times = 10),
         Subject = NA))

#predict probabilities for surrender, use fitted to get upper and lower quantile measures in probabilities
fit <-
  fitted(m_0, newdata = nd, re_formula = ~ (0 + Follower_gender | Subject )) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd) 

pred <-
  predict(m_0, newdata = nd, re_formula = ~ (0 + Follower_gender | Subject)) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd)

pred$Leader_gender <- as.character(pred$Leader_gender)
pred$Follower_gender <- as.character(pred$Follower_gender)
fit$Leader_gender <- as.character(fit$Leader_gender)
fit$Follower_gender <- as.character(fit$Follower_gender)


#Changing the genders
# fit$Follower_gender[fit$Follower_gender == 0] <- "Male"
# fit$Follower_gender[fit$Follower_gender == "1"] <- "Female"
# fit$Leader_gender[fit$Leader_gender == "0"] <- "Male"
# fit$Leader_gender[fit$Leader_gender == 1] <- "Female"
# 
# 
pred$Follower_gender[pred$Follower_gender == 0] <- "Male"
pred$Follower_gender[pred$Follower_gender == 1] <- "Female"
pred$Leader_gender[pred$Leader_gender == 0] <- "Male"
pred$Leader_gender[pred$Leader_gender == 1] <- "Female"

```


```{r H1 plot}
#create the plot
H1 <- ggplot(pool_disagree, aes(x = Leader_gender, y = Surrender, fill = Leader_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2"))
H1



```



#H2: there is a follower effect: leaders tend to surrender more to men than to women
```{r H2: there is a follower effect: leaders tend to surrender more to men than to women }

# H2: There is a follower effect: leaders tend to surrender more to men than to women
hypothesis(m_0, "(Leader_gender0:Follower_gender0 + Leader_gender1:Follower_gender0)/2 > (Leader_gender0:Follower_gender1 + Leader_gender1:Follower_gender1)/2")




```

# H2: plotting
```{r}

#create the plot
H2 <- ggplot(pool_disagree, aes(x = Follower_gender, y = Surrender, fill = Follower_gender)) +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "Hypothesis 2") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5))) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2"))

H2


```


```{r H3: there is an interaction, males are more discriminative as to their followers gender than females are }
# H3: There is an interaction: males are more discriminative as to their followers gender than females are

hypothesis(m_0, "(Leader_gender0:Follower_gender0 - Leader_gender0:Follower_gender1) > (Leader_gender1:Follower_gender0 - Leader_gender1:Follower_gender1)")

#tetstststst
hypothesis(m_0, "(Leader_gender0:Follower_gender0 - Leader_gender1:Follower_gender1) < (Leader_gender1:Follower_gender0 - Leader_gender1:Follower_gender1)")
```


# H3: plotting
```{r}

marginal_effects(m_0)
```


```{r}
#create the plot
H3.1 <- ggplot(pool_disagree, aes(x = Leader_gender, y = Surrender, fill = Follower_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 3 - Boxplot") +
  geom_boxplot(aes(x = Leader_gender, Estimate, fill = Follower_gender) , data = pred, width = 0.5, alpha = 0.8) + 
  labs(fill = "Follower gender") +
  theme(panel.grid.minor = element_blank()) +
  geom_hline(yintercept=h, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), h))) +
  scale_fill_manual(values=c("palegreen3", "gold2"))

H3.1

```


```{r}




H3.2 <- ggplot(pred, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, width = 0.7, alpha = 0.8) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5))) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 3") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("palegreen3", "gold2"))




H3.2
```



50 % linje 

boxplot lægger vægt på outliers 

violin med mean + confidence 

Males tend to underestimate themselves at the same level as females tend to underestimates themselves in relation to their own gender
  Not really equality bias, as it is not at 50 % - so they do not wiegh their own and their partner as equally good
  
  
  tilføj linjer mellem boxplots
  
  
  men god pointe er at skill-difference har indgået i modellen som om at deltagerne hele tiden ahr alt information om den anden partners evner 

```{r}
p <- predict(model_1.3, allow_new_levels = T, re_formula = ~ (1 | ID), sample_new_levels = "gaussian", newdata = nd, summary = FALSE)

#as dataframe
p <- as.data.frame(p)

#make dataframe with diagnosis and predicted estimates 
diag0 <- subset(p, select = V1)

diag0$diagnosis <- 0

names(diag0) <- c("Estimate", "diagnosis")

diag1 <- subset(p, select = V2)

diag1$diagnosis <- 1

names(diag1) <- c("Estimate", "diagnosis")

pred_data <- rbind(diag0, diag1)

pred_data$diagnosis <- as.factor(pred_data$diagnosis)

#create the plot
bee <- ggplot(data, aes(x = diagnosis, y = PitchSD_z)) +
  geom_violin(aes(x = diagnosis, y = Estimate), data = pred_data, trim = FALSE) + 
  ylim(-3,3) + 
  geom_quasirandom(alpha = 0.5, colour = "dark red") +
  labs(x = "diagnosis", y = "Pitch", title = "Flot plot") + 
  geom_boxplot(aes(x = diagnosis, y = Estimate), data = pred_data, width = 0.12) 

  
bee
```



```{r}

#pool_disagree$Surrender <- as.numeric(pool_disagree$Surrender)

# plotting the fitted regression lines
ggplot(fit, aes(x = Leader_gender, y = Estimate, col = Follower_gender)) +
  geom_line() +
  #geom_point(data=pool_disagree, aes(x=Leader_gender,y=Surrender,color=Follower_gender)) + 
  xlim(low, high) +
  geom_smooth(data = fit, aes(y = Estimate, ymin = Q2.5, ymax = Q97.5, fill = Leader_gender),stat = "identity", alpha = 1/4, size = 1/2) 


summary(m_answer)

```




