---
title: "Models"
author: "MM"
date: "13/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Preparing markdown
```{r setting working directory}
#set working directory 
#setwd("C:/Users/KK/OneDrive - Aarhus Universitet/Dokumenter/MM, udgives/gender_bias_in_decision_making/Gender_bias_study_1") #Kiri
#setwd("~/gender_bias_in_decision_making/Gender_bias_study_1/") #Signe
setwd("~/gender_bias_in_decision_making/Gender_bias_study_1") #Thea
```

```{r loading libraries}
#load libraries
library(pacman)
p_load(lme4, lmerTest, brms, tidyverse, stringi, tm, ggrepel, ggbeeswarm, boot)
```

#Loading sensitivity scores (wide)
```{r load data}
#read csv files with estimates
data <- read.csv("data_disagree_long_sensitivity.csv")[,3:17]
data_long <- read.csv("data_long_sensitivity.csv")[,2:16]

```

#Data 
```{r}
#Changing the format of the leader and follower gender
data$Follower_gender <- as.factor(data$Follower_gender)
data$Leader_gender <- as.factor(data$Leader_gender)
```


##Model without skill difference (basic)
```{r model without skill difference}
#Defining priors
prior_basic <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
prior_check_basic <- brm(leader_behaviour ~ 0 + Leader_gender : Follower_gender + (0 + skill_dif_c:Follower_gender | Subject), prior = prior_basic, data = data, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_basic, nsamples = 100)

#model without skill difference
m_basic <- brm(
  leader_behaviour ~ 0 + Leader_gender : Follower_gender + (0 + skill_dif_c:Follower_gender | Subject),
  data = data,
  prior = prior_basic,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  chains=2,
  cores=2,
  control = list(adapt_delta = 0.99) 
) 

#Model summary and plots

summary(m_basic)
plot(m_basic)
marginal_effects(m_basic)

```


##The full model with skill difference (full)
```{r, eval = FALSE}
#Get priors
get_prior(leader_behaviour ~ 0 + skill_dif_c * Leader_gender:Follower_gender + (0 + skill_dif_c:Follower_gender | Subject ), data = data, family = "bernoulli")

#Defining priors
prior_full <- c(
  prior(normal(0,.2),class="b"),
  prior(normal(0,.1),class="sd")
)

#prior predictive check
prior_check_full <- brm(leader_behaviour ~ 0 + skill_dif_c * Leader_gender : Follower_gender + (0 + skill_dif_c:Follower_gender | Subject ), prior = prior_full, data = data, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_full, nsamples = 100)

# Model w skill difference
m_full <- brm(
  leader_behaviour ~ 0 + skill_dif_c * Leader_gender : Follower_gender + (0 + skill_dif_c:Follower_gender | Subject),
  data = data,
  prior = prior_full,
  sample_prior=T,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2,
  control = list(adapt_delta = 0.99) #only for answer model, due to Eff.Sample
) 

summary(m_full)
plot(m_full)
marginal_effects(m_full)
```


#Model comparison
```{r, eval = FALSE}
waic(m_full, m_basic)

```


#Alternative hypothesis: Are men better than women?
##Modelling: Are men better than women?
```{r}
#Defining priors
prior_mf <- c(
  prior(normal(0, 0.2),class="Intercept"),
  prior(normal(0,0.1),class="b"),
  prior(normal(0,0.2), class= "sd", coef = "dif_blue", group = "Subject"),
  prior(normal(0,0.1), class= "sd", coef = "Intercept", group = "Subject")
)

#prior predictive check
prior_check_mf <- brm(answer ~ dif_blue*Gender + (1+dif_blue|Subject), prior = prior_mf, data = data_long, sample_prior = "only",iter = 4000, family = "bernoulli", chains = 2, cores = 2)

pp_check(prior_check_mf, nsamples = 100)

# Model w skill difference
skill_mf <- brm(
  answer ~ dif_blue*Gender + (1+dif_blue|Subject), 
  data = data_long,
  prior = prior_mf,
  family = "bernoulli",
  sample_prior=T,
  seed = 123, # Adding a seed makes results reproducible.
  cores=2,
  chains=2
) 

summary(skill_mf)
plot(skill_mf)
marginal_effects(skill_mf)

```

##Hypothesis testing: Men perform better than women
```{r}
#Men perform better than women
hypothesis(skill_mf, "dif_blue < (dif_blue+dif_blue:GenderMale)")

hypothesis(skill_mf, "dif_blue < (dif_blue+dif_blue:GenderMale)")

hypothesis(skill_mf, "dif_blue > (dif_blue+dif_blue:GenderMale)")

#No

```


#Hypothesis testing: H1 and H2

# H1: There is a leader effect: male leaders tend to surrender less than female leaders
```{r H1}
#H1: In general male leaders tend to surrender less than female leaders
hypothesis(m_basic, "(Leader_gender0:Follower_gender0 + Leader_gender0:Follower_gender1)/2 < (Leader_gender1:Follower_gender0 + Leader_gender1:Follower_gender1)/2")


#full model
#hypothesis(m_full, "(Leader_gender0:Follower_gender0 + Leader_gender0:Follower_gender1)/2 < (Leader_gender1:Follower_gender0 + Leader_gender1:Follower_gender1)/2")

```

##H1: Plotting
```{r preparing predictions}
#create newdata to make predictions from 
nd <- 
  expand.grid(tibble(
         Follower_gender=factor(0:1) %>% rep(., times = 10),
         Leader_gender = factor(0:1) %>% rep(., times = 10),
         Subject = NA))

#Predicting new values from the basic model
pred <-
  predict(m_basic, newdata = nd, re_formula = ~ (0 + Follower_gender | Subject)) %>%  # we can use the same nd data from last time
  as_tibble() %>%
  bind_cols(nd)

#Changing the format of the follower and leader gender
pred$Leader_gender <- as.character(pred$Leader_gender)
pred$Follower_gender <- as.character(pred$Follower_gender)

#Changing the genders from dummy coding
pred$Follower_gender[pred$Follower_gender == 0] <- "Male"
pred$Follower_gender[pred$Follower_gender == 1] <- "Female"
pred$Leader_gender[pred$Leader_gender == 0] <- "Male"
pred$Leader_gender[pred$Leader_gender == 1] <- "Female"
```

```{r H1 plot}
#Creating a rounding function for plots
rounding <- function(x) sprintf("%.3f", x)

#create the plot
H1 <- ggplot(data, aes(x = Leader_gender, y = leader_behaviour, fill = Leader_gender)) +
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Hypothesis 1") +
  geom_boxplot(aes(x = Leader_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5)), labels = rounding) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2")) +
  theme(plot.title = element_text(hjust = 0.5))

H1
```


#H2:There is a follower effect: leaders tend to surrender more to men than to women
```{r H2: there is a follower effect: leaders tend to surrender more to men than to women }
# H2: There is a follower effect: leaders tend to surrender more to men than to women
hypothesis(m_basic, "(Leader_gender0:Follower_gender0 + Leader_gender1:Follower_gender0)/2 > (Leader_gender0:Follower_gender1 + Leader_gender1:Follower_gender1)/2")

#testing the effect of inv.logit before hyp
hypothesis(m_basic, "(inv.logit(Leader_gender0:Follower_gender0) + inv.logit(Leader_gender1:Follower_gender0))/2 > (inv.logit(Leader_gender0:Follower_gender1) + inv.logit(Leader_gender1:Follower_gender1))/2")

#hypothesis(m_full, "(Leader_gender0:Follower_gender0 + Leader_gender1:Follower_gender0)/2 > (Leader_gender0:Follower_gender1 + Leader_gender1:Follower_gender1)/2")
```

##H2: Plotting
```{r}
#create the plot
H2 <- ggplot(data, aes(x = Follower_gender, y = leader_behaviour, fill = Follower_gender)) +
  labs(x = "Follower gender", y = "Predicted propensity to surrender", title = "Hypothesis 2") +
  geom_boxplot(aes(x = Follower_gender, Estimate) , data = pred, width = 0.5) + 
  theme(legend.position = "none", panel.grid.minor = element_blank()) + 
  geom_violin(aes(x = Follower_gender, y = Estimate), data = pred, trim = FALSE, width =1, alpha = 0.1) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5)), labels = rounding) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_fill_manual(values=c("palegreen3", "gold2"))+
  theme(plot.title = element_text(hjust = 0.5))

H2
```


##both hypotheses visualized
```{r}
main_plot <- ggplot(pred, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, width = 0.7, alpha = 0.8) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(min(pred$Estimate), max(pred$Estimate), length.out=5), 0.5)), labels = rounding) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Predicted propensity to surrender", title = "Both hypotheses") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("palegreen3", "gold2"))+
  theme(plot.title = element_text(hjust = 0.5))

main_plot

```

```{r}
#Test

thea_plot <- ggplot(pred, aes(x = Leader_gender, y = Estimate, fill = Follower_gender)) + 
  geom_violin(aes(x = Leader_gender, y = Estimate), data = pred, width = 0.7, alpha = 0.8) + 
  geom_hline(yintercept= 0.5, color = "black", linetype = "dashed", alpha = 0.8) + 
  scale_y_continuous(breaks = sort(c(seq(0.475, 0.575, length.out=5), 0.5)), labels = rounding) + 
  theme(panel.grid.minor = element_blank()) + 
  labs(x = "Leader gender", y = "Propensity to surrender", title = "TITLE?") + 
  stat_summary(fun.data=mean_sdl, geom="pointrange", color="black", position = position_dodge(width = 0.7), alpha = 0.8) +
  labs(fill = "Follower gender") + 
  scale_fill_manual(values=c("palegreen3", "gold2"))+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.title = element_text(color = "black", size = 16, face="bold"), legend.text = element_text(color = "black", size = 16)) +
  theme(axis.text=element_text(size=14),axis.title=element_text(size=16,face="bold"))
 

thea_plot

```




