---
title: "DataCleaning"
author: "Signe Kløve Kjær"
date: "2/5/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Loading packages
```{r loading packages, include = FALSE}
library(brms);library(tidyverse); library(tidybayes); library(ggplot2); library(LaplacesDemon); library(tidyr); library(reshape2);library(pacman); library(tibble);library(tidyr);

```


#Define path
```{r}
#Defining path
data_path = ("~/SocKultExam/Data/") #Kiri

#Thea
#setwd("~/SocKultExam")
#data_path = ("Data/") 

#Signe
#data_path = ("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/Data/")
```


#Loading data and merging
```{r loading main data include = FALSE}
#Listing files in path
files <- list.files(path = data_path)

#Create empty data frame
data <- data.frame(matrix(ncol = 36, nrow = 0))

#Looping through data files and inserting in dataframe
for (i in files) {
  d <- read.delim(file = paste(data_path, i, sep = ""), sep = ",", header = TRUE)
  data = rbind(data,d)
}

```

```{r loading data with different amount of trials}
#Setting different path for extraordinary files
#kiri_path = ("~/SocKultExam/") #Thea
kiri_path = ("~/SocKultExam/kiri/")#Kiri
#kiri_path = ("/Users/signeklovekjaer/Documents/CognitiveScience/4.semester/Social_and_cultural_dynamics_in_cognition/Exam/SocKultExam/") #Signe

#Listing files in directory
kiri_files <- list.files(path = kiri_path, pattern = "*.csv") 

#Creating empty data frame
kiri_data <- data.frame(matrix(ncol = 35, nrow = 0))

#Looping through Kiri data 
for (i in kiri_files) {
  d <- read.delim(file = paste(kiri_path, i, sep = ""), sep = ",", header = TRUE, stringsAsFactors = FALSE)
  kiri_data = rbind(kiri_data, d)
}

```


```{r}
#Merge the two dataframes
kiri_data <- add_column(kiri_data, Computer = "Two screens", .after = 4)
data <- rbind(data, kiri_data)
```


#Data cleaning
```{r cleaning data, include = FALSE}

#Removing column of x
data <- subset(data, select = -c(X))

#Cleaning group numbers
data$GroupNumber[data$GroupNumber == "17_10_30"] <- 17
data$GroupNumber[data$GroupNumber == "18_10_30"] <- 18
data$GroupNumber[data$GroupNumber == "19_10_50"] <- 19
data$GroupNumber[data$GroupNumber == "20_10_50"] <- 20
data$GroupNumber[data$GroupNumber == "21_12_15"] <- 21
data$GroupNumber[data$GroupNumber == "22_12_15"] <- 22
data$GroupNumber[data$GroupNumber == "23_12_40"] <- 23
data$GroupNumber[data$GroupNumber == "24_12_40"] <- 24
data$GroupNumber[data$GroupNumber == "25_15_00"] <- 25
data$GroupNumber[data$GroupNumber == "26_15_00"] <- 26
data$GroupNumber[data$GroupNumber == "27_15_20"] <- 27
data$GroupNumber[data$GroupNumber == "28_15_20"] <- 28
data$GroupNumber[data$GroupNumber == "29_16_00"] <- 29
data$GroupNumber[data$GroupNumber == "30_16_00"] <- 30
data$GroupNumber[data$GroupNumber == "31_16_20"] <- 31
data$GroupNumber[data$GroupNumber == "32_16_20"] <- 32
data$GroupNumber[data$GroupNumber == "33_9_30"] <- 33
data$GroupNumber[data$GroupNumber == "34_09_30"] <- 34
data$GroupNumber[data$GroupNumber == "35_09_50"] <- 35
data$GroupNumber[data$GroupNumber == "36_9_50"] <- 36
data$GroupNumber[data$GroupNumber == "37_26_4"] <- 37
data$GroupNumber[data$GroupNumber == "38_26_4"] <- 38
data$GroupNumber[data$GroupNumber == "39_26_4"] <- 39
data$GroupNumber[data$GroupNumber == "40_26_4"] <- 40

#Cleaning subject IDs
data$SubjectID_left <- as.character(data$SubjectID_left)
data$SubjectID_right <- as.character(data$SubjectID_right)
data$SubjectID_left[data$SubjectID_left == "steph"] <- "stephanie"
data$SubjectID_right[data$SubjectID_right == "Emil"] <- "emil"
data$SubjectID_right[data$SubjectID_right == "Sebber"] <- "seb"
data$SubjectID_left[data$SubjectID_left == "signe"] <- "SigneR"
data$SubjectID_right[data$SubjectID_right == "karo"] <- "Karoline"
data$SubjectID_right[data$SubjectID_right == "tobias"] <- "Toby"
data$SubjectID_left[data$SubjectID_left == "Nina"] <- "nina"
data$SubjectID_right[data$SubjectID_right == "theasmom"] <- "Theasmom"
data$SubjectID_left[data$SubjectID_left == "emma"] <- "Emma"
data$SubjectID_right[data$SubjectID_right == "LasseKob"] <- "Lasse"
```

##Adding difficulty variable og dummy coding
```{r making variables for sensitivty, include = FALSE}
#Making unique subjects
data$unique_ID_right <- paste(data$GroupNumber, data$SubjectID_right, sep = "_")
data$unique_ID_left <- paste(data$GroupNumber, data$SubjectID_left, sep = "_")

#Making column, which expresses difficulty
data$dif_blue <- data$Prop_blue_image_2 - data$Prop_blue_image_1
data$dif_blue_abs <- abs(data$Prop_blue_image_2 - data$Prop_blue_image_1)

#Making a column, which expresses answer of participants, 0 = left picture, 1 = right picture
data$right_answer <- ifelse(data$Response_right > 0, 1, 0)
data$left_answer <- ifelse(data$Response_left > 0, 1, 0)

#Joining joint answer to one column
data$joint_answer <- data$Joint_right+ data$Joint_left

#Recoding joint answer to be 0 and 1's, 0 right, 1 left, NA = no leader
data$joint_answer[data$joint_answer == 0] <- NA #Replacing 0's with NA
data$joint_answer[data$joint_answer == -1] <- 0
```


##Adding variables: Agree, chosen leader and gender
```{r coding for leader/follower}

#create a column that sorts out all the agreed trials
data$chosen_leader <- ifelse(data$right_answer == data$left_answer, "Agree", 0) 

#Create variable, which determines the chosen leader
data$chosen_leader[data$chosen_leader == 0 & data$Joint_right == 0] <- "Left_lead"
data$chosen_leader[data$chosen_leader == 0 & data$Joint_left == 0] <- "Right_lead"

#create column that specifies the gender of the leader
data$Leader_gender <- 0
data$Leader_gender <- ifelse(data$chosen_leader == "Left_lead", as.character(data$Gender_left), as.character(data$Gender_right))
data$Leader_gender[data$chosen_leader == "Agree"] <- NA

#create column that specifies the gender of the follower
data$Follower_gender <- 0
data$Follower_gender <- ifelse(data$chosen_leader == "Left_lead", as.character(data$Gender_right), as.character(data$Gender_left))
data$Follower_gender[data$chosen_leader == "Agree"] <- NA

```

#Adding variable: Stick/surrender
```{r Did the leader stick?}
#leader stubbornness
data$Stubborn_leader <- 0 #Creating column of 0's

data$Stubborn_leader[data$chosen_leader == "Right_lead" & data$joint_answer == data$right_answer] <- "stick" #Inserting cases were leader stick for right leader
data$Stubborn_leader[data$chosen_leader == "Right_lead" & data$joint_answer != data$right_answer] <- "surrender" #Inserting cases were leader surrender for right leader

data$Stubborn_leader[data$chosen_leader == "Left_lead" & data$joint_answer == data$left_answer] <- "stick" #Inserting cases were leader stick for left leader
data$Stubborn_leader[data$chosen_leader == "Left_lead" & data$joint_answer != data$left_answer] <- "surrender" #Inserting cases were leader surreder for left leader

data$Stubborn_leader[data$chosen_leader == "Agree"] <- NA #Removing cases were they agree

```

```{r Plotting the effect of stick or surrender, leader and follower gender}
#Filtering data to include only joint decisions
disagree_data <- na.omit(data)

#Making one column specifying the leader and follower gender
disagree_data$Leader_Follower <- paste("Leader:", disagree_data$Leader_gender, "_Follower:", disagree_data$Follower_gender, sep = "")

#Recoding stick to 0 and 1, stick = 1, 0 = surrender
disagree_data$stick <- ifelse(disagree_data$Stubborn_leader == "stick", 1, 0)

#Plotting the count 
ggplot(data = disagree_data, aes(Stubborn_leader, fill = Stubborn_leader)) +
  facet_grid(~Leader_Follower) +
  geom_histogram(stat = "count")

```

Bayesian tutorial on logistic regression: https://www.jamesrrae.com/post/bayesian-logistic-regression-using-brms-part-1/

#NO POOLING

###Individual performance

```{r logistic regression using wide format, individual left}

###LEFT

#Getting priors
get_prior(left_answer ~ dif_blue, data = data, family = "bernoulli")
get_prior(Correct_left ~ 0 +dif_blue_abs, data = data, family = "bernoulli")

#Making a number of iterations variable
n = 1

###Making a loop for individual slope
for (i in unique(data$unique_ID_left)){
  data_i <- filter(data, unique_ID_left == i) #Choosing temporary data
  
  #Defining paths for plots
  trans_left_path = file.path("~/SocKultExam/plots/transition/left/", paste("trans_left_plot_", i, ".jpeg", sep = ""))
  pp_left_path = file.path("~/SocKultExam/plots/pp_check/left/", paste("pp_left_plot_",i, ".jpeg", sep = ""))
  marginal_left_path = file.path("~/SocKultExam/plots/marginal/left/", paste("marginal_left_plot_", i, ".jpeg", sep = ""))
  #...and for correct
  correct_trans_left_path = file.path("~/SocKultExam/plots/correct_transition/left/", paste("correct_trans_left_plot_", i, ".jpeg", sep = ""))
  correct_pp_left_path = file.path("~/SocKultExam/plots/correct_pp_check/left/", paste("correct_pp_left_plot_",i, ".jpeg", sep = ""))
  correct_marginal_left_path = file.path("~/SocKultExam/plots/correct_marginal/left/", paste("correct_marginal_left_plot_", i, ".jpeg", sep = ""))
  
  #Defining priors
  prior =  c(
  prior(normal(0,0.17), class = "Intercept"),  #Why does this not work? 
  prior(normal(0,0.125), class = "b", coef = "dif_blue")
  )
  
  #...and for correct
  correct_prior =  c(
  prior(normal(0,0.25), class = "b", coef = "dif_blue_abs")
  )
  
  
  #Prior predictive check
  prior_check <- brm( left_answer ~ dif_blue, prior = prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")
  
    #Prior predictive check
  correct_prior_check <- brm(Correct_left ~ 0 + dif_blue_abs, prior = correct_prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")
 
  #Making the model - using answer
  m <- brm(
    left_answer ~ dif_blue,
    data = data_i,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
 
  
  #Making the model - using correctness
  m_c <- brm(
    Correct_left ~ 0 + dif_blue_abs,
    data = data_i,
    prior = correct_prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
 
  
   
  #Marginal effects plot: Plotted and saved
  jpeg(file=marginal_left_path)
  print(marginal_effects(m))
  dev.off()
  
  #Transition plot: plotted and saved
  jpeg(file=trans_left_path)
  print(plot(m))
  dev.off()

  #pp_check plot: Plotted and saved
  jpeg(file=pp_left_path)
  print(pp_check(prior_check, nsamples = 100))
  dev.off()
  
  #model with correct
   
  #Marginal effects plot: Plotted and saved
  jpeg(file=correct_marginal_left_path)
  print(marginal_effects(m_c))
  dev.off()
  
  #Transition plot: plotted and saved
  jpeg(file=correct_trans_left_path)
  print(plot(m_c))
  dev.off()

  #pp_check plot: Plotted and saved
  jpeg(file=correct_pp_left_path)
  print(pp_check(correct_prior_check, nsamples = 100))
  dev.off()
   
  summary(m)
  summary(m_c)
  
  #Saving summary in temporary dataframe
  data_i$Est_int_left <- fixef(m)[1]
  data_i$Error_int_left <- fixef(m)[3]
  data_i$Est_dif_blue_left <- fixef(m)[2]
  data_i$Error_dif_blue_left <- fixef(m)[4]
  data_i$Est_int_left_correct <- fixef(m_c)[1]
  data_i$Error_int_left_correct <- fixef(m_c)[3]
  data_i$Est_dif_blue_left_correct <- fixef(m_c)[2]
  data_i$Error_dif_blue_left_correct <- fixef(m_c)[4]
  data_i$Rhat_1_left <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[1]]
  data_i$Rhat_2_left <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[2]]
  data_i$Rhat_3_left <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[3]] #Why are there three? 
  data_i$Ess_1_left <- m[["fit"]]@.MISC[["summary"]][["ess"]][[1]]
  data_i$Ess_2_left <- m[["fit"]]@.MISC[["summary"]][["ess"]][[2]]
  data_i$Ess_3_left <- m[["fit"]]@.MISC[["summary"]][["ess"]][[3]] #Why are there three? 
  
  #Insert into permanent data frame
  if (n == 1){
    Results <- data_i
  } else {
    Results <- rbind(Results, data_i)
  }

  #Adding 1 to number of iterations
n = n + 1
  
}

write.csv(Results, file = "Results_left.csv")


```

```{r logistic regression using wide format, individual right}
###RIGHT

#Making a number of iterations variable
n = 1

###Making a loop for individual slope
for (i in unique(data$unique_ID_right)){
  data_i <- filter(data, unique_ID_right == i) #changed from data_i <- filter(Results, unique_ID_right == i)
  
  #Defining paths for plots
  trans_right_path = file.path("~/SocKultExam/plots/transition/right/", paste("trans_right_plot_", i, ".jpeg", sep = ""))
  pp_right_path = file.path("~/SocKultExam/plots/pp_check/right/", paste("pp_right_plot_",i, ".jpeg", sep = ""))
  marginal_right_path = file.path("~/SocKultExam/plots/marginal/right/", paste("marginal_right_plot_", i, ".jpeg", sep = ""))
  
  #...and for correct
  correct_trans_right_path = file.path("~/SocKultExam/plots/correct_transition/right/", paste("correct_trans_right_plot_", i, ".jpeg", sep = ""))
  correct_pp_right_path = file.path("~/SocKultExam/plots/correct_pp_check/right/", paste("correct_pp_right_plot_",i, ".jpeg", sep = ""))
  correct_marginal_right_path = file.path("~/SocKultExam/plots/correct_marginal/right/", paste("correct_marginal_right_plot_", i, ".jpeg", sep = ""))
  
  #Defining priors
  prior =  c(
  prior(normal(0,0.17), class = "Intercept"),  #Why does this not work? 
  prior(normal(0,0.125), class = "b", coef = "dif_blue")
  )
  
  #...and for correct
  correct_prior =  c(
  prior(normal(0,0.25), class = "b", coef = "dif_blue_abs")
  )
  
  
    #Prior predictive check
  prior_check <- brm(right_answer ~ dif_blue, prior = prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")
  
    #Prior predictive check
  correct_prior_check <- brm( Correct_right ~ 0 + dif_blue_abs, prior = correct_prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")

    #Making the model - using answer
  m <- brm(
    right_answer ~ dif_blue,
    data = data_i,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
 
  
  #Making the model - using correctness
  m_c <- brm(
    Correct_right ~ 0 + dif_blue_abs,
    data = data_i,
    prior = correct_prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
  
  #Marginal effects plot: Plotted and saved
  jpeg(file=marginal_right_path)
  print(marginal_effects(m))
  dev.off()
  
  #transition plot: Plotted and saved
  jpeg(file=trans_right_path)
  print(plot(m))
  dev.off()

  #pp_check plot: Plotted and saved
  jpeg(file=pp_right_path)
  print(pp_check(prior_check, nsamples = 100))
  dev.off()
  
  #model with correct
   
  #Marginal effects plot: Plotted and saved
  jpeg(file=correct_marginal_right_path)
  print(marginal_effects(m_c))
  dev.off()
  
  #Transition plot: plotted and saved
  jpeg(file=correct_trans_right_path)
  print(plot(m_c))
  dev.off()

  #pp_check plot: Plotted and saved
  jpeg(file=correct_pp_right_path)
  print(pp_check(correct_prior_check, nsamples = 100))
  dev.off()
   
  
  summary(m)
  summary(m_c)
  
  
  #Saving summary in temporary dataframe
  data_i$Est_int_right <- fixef(m)[1]
  data_i$Error_int_right <- fixef(m)[3]
  data_i$Est_dif_blue_right <- fixef(m)[2]
  data_i$Error_dif_blue_right <- fixef(m)[4]
  data_i$Est_int_right_correct <- fixef(m_c)[1]
  data_i$Error_int_right_correct <- fixef(m_c)[3]
  data_i$Est_dif_blue_right_correct <- fixef(m_c)[2]
  data_i$Error_dif_blue_right_correct <- fixef(m_c)[4]
  data_i$Rhat_1_right <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[1]]
  data_i$Rhat_2_right <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[2]]
  data_i$Rhat_3_right <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[3]] #Why are there three?
  data_i$Ess_1_right <- m[["fit"]]@.MISC[["summary"]][["ess"]][[1]]
  data_i$Ess_2_right <- m[["fit"]]@.MISC[["summary"]][["ess"]][[2]]
  data_i$Ess_3_right <- m[["fit"]]@.MISC[["summary"]][["ess"]][[3]] #Why are there three?
  
  #Insert into permanent data frame
  if (n == 1){
    Results <- data_i
  } else {
    Results <- rbind(Results, data_i)
  }
  
n = n + 1
  
}

write.csv(Results, file = "Results_left_and_right.csv")

```

###Joint performance
```{r logistic regression using wide format, joint}
###JOINT

#Making a number of iterations variable
n = 1

###Making a loop for individual slope
for (i in unique(data$GroupNumber)){
  data_i <- filter(data, GroupNumber == i)
  
  #Defining paths for plots
  trans_joint_path = file.path("~/SocKultExam/plots/transition/joint/", paste("trans_joint_plot_", i, ".jpeg", sep = ""))
  pp_joint_path = file.path("~/SocKultExam/plots/pp_check/joint/", paste("pp_joint_plot_",i, ".jpeg", sep = ""))
  marginal_joint_path = file.path("~/SocKultExam/plots/marginal/joint/", paste("marginal_joint_plot_", i, ".jpeg", sep = ""))
  
  #...and for correct
  correct_trans_joint_path = file.path("~/SocKultExam/plots/correct_transition/joint/", paste("correct_trans_joint_plot_", i, ".jpeg", sep = ""))
  correct_pp_joint_path = file.path("~/SocKultExam/plots/correct_pp_check/joint/", paste("correct_pp_joint_plot_",i, ".jpeg", sep = ""))
  correct_marginal_joint_path = file.path("~/SocKultExam/plots/correct_marginal/joint/", paste("correct_marginal_joint_plot_", i, ".jpeg", sep = ""))
  
  #Defining priors
  prior =  c(
  prior(normal(0,0.17), class = "Intercept"),  #Why does this not work? 
  prior(normal(0,0.125), class = "b", coef = "dif_blue")
  )
  
  #...and for correct
  correct_prior =  c(
  prior(normal(0,0.25), class = "b", coef = "dif_blue_abs")
  )
  
    #Prior predictive check
  prior_check <- brm(joint_answer ~ dif_blue, prior = prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")
  
    #Prior predictive check
  correct_prior_check <- brm( Correct_joint ~ 0 + dif_blue_abs, prior = correct_prior,
           data = data_i, sample_prior = "only",iter = 4000, family = "bernoulli")

      #Making the model - using answer
  m <- brm(
    joint_answer ~ dif_blue,
    data = data_i,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 
 
  #Making the model - using correctness
  m_c <- brm(
    Correct_joint ~ 0 + dif_blue_abs,
    data = data_i,
    prior = correct_prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
  ) 

  #Marginal plot
  jpeg(file=marginal_joint_path)
  print(marginal_effects(m))
  dev.off()
  
  #transition plot: Plotted and saved
  jpeg(file=trans_joint_path)
  print(plot(m))
  dev.off()

  #pp_check plot: Plotted and saved
  jpeg(file=pp_joint_path)
  print(pp_check(prior_check, nsamples = 100))
  dev.off()
  
  #Model with correct
   
  #Marginal effects plot: Plotted and saved
  jpeg(file=correct_marginal_joint_path)
  print(marginal_effects(m_c))
  dev.off()
  
  #Transition plot: plotted and saved
  jpeg(file=correct_trans_joint_path)
  print(plot(m_c))
  dev.off()

  #pp_check plot: Plotted and saved
  jpeg(file=correct_pp_joint_path)
  print(pp_check(correct_prior_check, nsamples = 100))
  dev.off()
  summary(m)
  
  #Saving summary in temporary dataframe
  data_i$Est_int_joint <- fixef(m)[1]
  data_i$Error_int_joint <- fixef(m)[3]
  data_i$Est_dif_blue_joint <- fixef(m)[2]
  data_i$Error_dif_blue_joint <- fixef(m)[4]
  data_i$Est_int_joint_correct <- fixef(m_c)[1]
  data_i$Error_int_joint_correct <- fixef(m_c)[3]
  data_i$Est_dif_blue_joint_correct <- fixef(m_c)[2]
  data_i$Error_dif_blue_joint_correct <- fixef(m_c)[4]
  data_i$Rhat_1_joint <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[1]]
  data_i$Rhat_2_joint <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[2]]
  data_i$Rhat_3_joint <- m[["fit"]]@.MISC[["summary"]][["rhat"]][[3]] #Why are there three?
  data_i$Ess_1_joint <- m[["fit"]]@.MISC[["summary"]][["ess"]][[1]]
  data_i$Ess_2_joint <- m[["fit"]]@.MISC[["summary"]][["ess"]][[2]]
  data_i$Ess_3_joint <- m[["fit"]]@.MISC[["summary"]][["ess"]][[3]] #Why are there three?
  
  #Insert into permanent data frame
  if (n == 1){
    Results <- data_i
  } else {
    Results <- rbind(Results, data_i)
  }
  
#Adding to the number of iterations
n = n + 1
  
}

write.csv(Results, file = "Results_left_right_joint.csv")

```


#Partial pooling

We need one column containing answer from both left and right in order to allow pooling between all participants

```{r making long format, include = FALSE}
#Subsetting the left data
left <- subset(data, select = c(GroupNumber, unique_ID_left, dif_blue, left_answer, joint_answer, Correct_left, Correct_joint, dif_blue_abs))

#Changing names
names(left) <- c("GroupNumber", "unique", "dif_blue", "answer", "joint_answer", "Correct", "Correct_joint", "dif_blue_abs")

#Subsetting right data
right <- subset(data, select = c(GroupNumber, unique_ID_right, dif_blue, right_answer, joint_answer, Correct_left, Correct_joint, dif_blue_abs))

#Chainging names
names(right) <- c("GroupNumber", "unique", "dif_blue", "answer", "joint_answer", "Correct", "Correct_joint", "dif_blue_abs")

#Removing half the joint data to inform the model, there is only one. 
right$Correct_joint <- NA
right$joint_answer <- NA

#Joining the dataframes
ldata <- rbind(left, right)

#Setting NA in correct answers
ldata$Correct_joint[is.na(ldata$joint_answer)] <- NA


```

When we have the long format, we can do a model with partial pooling: get_prior(answer ~ dif_blue + unique_ID, data = data)

A consideration: Should we allow different slopes for the same participant in different groups? 
- Yes, this makes more sense, when calculating performance difference. 

OBS: Needs discussion
- When saving the betas, we do not want the main effect of difficulty, can we just add that to the beta for the individual slope? 


- I think not, since it is in the scale of log odds. This is probably, what Riccardo is talking about. 

```{r creating model with partial pooling, individual}

#Getting priors
get_prior(answer ~ dif_blue + (1+ dif_blue|unique), family = "bernoulli", data = ldata)
get_prior(Correct ~ 0 + dif_blue + (0+ dif_blue|unique), family = "bernoulli", data = ldata)

#Defining priors
prior_answer =  c(
  prior(normal(0,0.125), class = "b", coef = "dif_blue"),
  prior(normal(0,0.17), class = "Intercept"),
  prior(normal(0,0.125), class = "sd", coef = "dif_blue", group = "unique"),
  prior(normal(0,0.17), class = "sd", coef = "Intercept", group = "unique")
)

prior_correct =  c(
  prior(normal(0,0.25), class = "b", coef = "dif_blue_abs"),
  prior(normal(0,0.25), class = "sd", coef = "dif_blue_abs", group = "unique")
)

 
  
#Defining paths for plots
trans_path_pool_indi = file.path("~/SocKultExam/plots/transition/pool/trans_plot_pool_individual.jpeg")
pp_path_pool_indi = file.path("~/SocKultExam/plots/pp_check/pool/pp_plot_pool_individual.jpeg")
marginal_path_pool_indi = file.path("~/SocKultExam/plots/marginal/pool/marginal_plot_pool_individual.jpeg")
#...and for correct
correct_trans_path_pool_indi = file.path("~/SocKultExam/plots/correct_transition/pool/correct_trans_plot_pool_individual.jpeg")
correct_pp_path_pool_indi = file.path("~/SocKultExam/plots/correct_pp_check/pool/correct_pp_plot_pool_individual.jpeg")
correct_marginal_path_pool_indi = file.path("~/SocKultExam/plots/correct_marginal/pool/correct_marginal_plot_pool_individual.jpeg")
  


#Prior predictive check - for answer
prior_check_answer_pool_individual <- brm( answer ~ dif_blue + (dif_blue|unique), prior = prior_answer,
           data = ldata, sample_prior = "only",iter = 4000, family = "bernoulli")

#Prior predictive check - for correct
prior_check_correct_pool_individual <- brm(Correct ~  0 + dif_blue_abs + (0 +dif_blue_abs|unique), prior = prior_correct,
           data = ldata, sample_prior = "only",iter = 4000, family = "bernoulli")



#Making the model - using answer
m_p <- brm(
  answer ~ dif_blue + (1+dif_blue|unique),
  data = ldata,
  prior = prior_answer,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
) 

#Making the model - using correct
m_p_c <- brm(
  Correct ~ 0 +dif_blue_abs + (0+dif_blue_abs|unique),
  data = ldata,
  prior = prior_correct,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
) 


  
#Marginal effects plot: Plotted and saved
jpeg(file=marginal_path_pool_indi)
print(marginal_effects(m_p))
dev.off()
    
  
#transition plot: Plotted and saved
jpeg(file=trans_path_pool_indi)
print(plot(m_p))
dev.off()

#pp_check plot: Plotted and saved
jpeg(file=pp_path_pool_indi)
print(pp_check(prior_check_answer_pool_individual, nsamples = 100))
dev.off()
  
  
#For correct
#Marginal effects plot: Plotted and saved
jpeg(file=correct_marginal_path_pool_indi)
print(marginal_effects(m_p_c))
dev.off()
    
#transition plot: Plotted and saved
jpeg(file=correct_trans_path_pool_indi)
print(plot(m_p_c))
dev.off()

#pp_check plot: Plotted and saved
jpeg(file=correct_pp_path_pool_indi)
print(pp_check(prior_check_correct_pool_individual, nsamples = 100))
dev.off()
  
###Saving the estimates

#ANSWER
#Saving random effect for individual 
pooling_individual_ranef <- as.data.frame(ranef(m_p))[,1:2] #Intercept

pooling_individual_ranef <- cbind(pooling_individual_ranef, as.data.frame(ranef(m_p))[,5:6]) #Slope

#Adding fixed effects to random effect
pooling_individual_fixef <- as.data.frame(fixef(m_p)) #Making data frame of fixed effects

pooling_individual$Intercept_ranef_fixef_estimate_answer <- pooling_individual_ranef[, 1] + pooling_individual_fixef[1, 1] #Adding fixef of intercept to ranef of intercept

pooling_individual$Slope_ranef_fixef_estimate_answer <- pooling_individual_ranef[, 3] + pooling_individual_fixef[1, 2] #Adding fixef of slope to ranef of slope

#CORRECT
#Saving random effect for individual 
pooling_individual_ranef <- as.data.frame(ranef(m_p_c))[,1:2] #Slope

#Adding fixed effects to random effect
pooling_individual_fixef <- as.data.frame(fixef(m_p_c)) #Making data frame of fixed effects

pooling_individual$Slope_ranef_fixef_estimate_correct <- pooling_individual_ranef[, 1] + pooling_individual_fixef[1, 1] #Adding fixef of slope to ranef of slope


#Adding rownames
pooling_individual <- cbind(Row.Names = rownames(pooling_individual_ranef), as.data.frame(pooling_individual))

write.csv(pooling_individual, file = "pooling_individual.csv")

```

```{r creating wide format, include = FALSE, this does not work}
#Merging ldata output with wide data frame
data$Group <-data$GroupNumber

#Inserting estimates in wide format
data$Intercept_pooling_rf_left[data$GroupNumber == unique(str_extract(pooling_individual$Row.Names, "\\d"))] <- pooling_individual$Intercept_ranef_fixef_estimate_answer[data$SubjectID_left == removeNumbers(gsub('[_]', '', pooling_individual$Row.Names))]


```


```{r creating model with partial pooling, joint, skal ikke bruges alligevel}
get_prior(joint_answer ~ dif_blue + (1 + dif_blue|GroupNumber), family = "bernoulli", data = ldata)
get_prior(Correct_joint ~ dif_blue_abs + (0 + dif_blue|GroupNumber), family = "bernoulli", data = ldata)

#Defining priors
prior_answer_joint =  c(
  prior(normal(0,0.125), class = "b", coef = "dif_blue"),
  prior(normal(0,0.17), class = "Intercept"),
  prior(normal(0,0.125), class = "sd", coef = "dif_blue", group = "GroupNumber"),
  prior(normal(0,0.17), class = "sd", coef = "Intercept", group = "GroupNumber")
)

prior_correct_joint =  c(
  prior(normal(0,0.25), class = "b", coef = "dif_blue_abs"),
  prior(normal(0,0.25), class = "sd", coef = "dif_blue_abs", group = "GroupNumber")
)

#Defining paths for plots
trans_path_pool_joint = file.path("~/SocKultExam/plots/transition/pool/trans_plot_pool_joint.jpeg")
pp_path_pool_joint = file.path("~/SocKultExam/plots/pp_check/pool/pp_plot_pool_joint.jpeg")
marginal_path_pool_joint = file.path("~/SocKultExam/plots/marginal/pool/marginal_plot_pool_joint.jpeg")
#...and for correct
correct_trans_path_pool_joint = file.path("~/SocKultExam/plots/correct_transition/pool/correct_trans_plot_pool_joint.jpeg")
correct_pp_path_pool_joint = file.path("~/SocKultExam/plots/correct_pp_check/pool/correct_pp_plot_pool_joint.jpeg")
correct_marginal_path_pool_joint = file.path("~/SocKultExam/plots/correct_marginal/pool/correct_marginal_plot_pool_joint.jpeg")
  

  
#Prior predictive check - for answer
prior_check_answer_pool_joint <- brm(joint_answer ~ dif_blue + (dif_blue|GroupNumber), prior = prior_answer_joint,
           data = ldata, sample_prior = "only",iter = 4000, family = "bernoulli")

#Prior predictive check - for correct
prior_check_correct_pool_joint <- brm(Correct_joint ~  0 + dif_blue_abs + (0 +dif_blue_abs|GroupNumber), prior = prior_correct_joint,
           data = ldata, sample_prior = "only",iter = 4000, family = "bernoulli")


#Joint model with answer
m_joint_answer <- brm(
  joint_answer ~ dif_blue + (1 + dif_blue|GroupNumber),
  data = ldata,
  prior = prior_answer_joint,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
  ) 
  
summary(m_joint_answer)

#Joint model with correct
m_joint_correct <- brm(
  Correct_joint ~ 0 + dif_blue_abs + (0+dif_blue_abs|GroupNumber),
  data = ldata,
  prior = prior_correct_joint,
  family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
  seed = 123 # Adding a seed makes results reproducible.
  
  ) 
summary(m_joint_correct)

  
#Marginal effects plot: Plotted and saved
jpeg(file=marginal_path_pool_joint)
print(marginal_effects(m_joint_answer))
dev.off()
    
  
#transition plot: Plotted and saved
jpeg(file=trans_path_pool_joint)
print(plot(m_joint_answer))
dev.off()

#pp_check plot: Plotted and saved
jpeg(file=pp_path_pool_joint)
print(pp_check(prior_check_answer_pool_joint, nsamples = 100))
dev.off()
  
  
#For correct
#Marginal effects plot: Plotted and saved
jpeg(file=correct_marginal_path_pool_joint)
print(marginal_effects(m_joint_correct))
dev.off()
    
#transition plot: Plotted and saved
jpeg(file=correct_trans_path_pool_joint)
print(plot(m_joint_correct))
dev.off()

#pp_check plot: Plotted and saved
jpeg(file=correct_pp_path_pool_joint)
print(pp_check(prior_check_correct_pool_joint, nsamples = 100))
dev.off()

#Saving estimates - runned till here!!

#ANSWER
#Saving random effect for individual 
pooling_joint_ranef <- as.data.frame(ranef(m_joint_answer))[,1:2] #Intercept

pooling_joint_ranef <- cbind(pooling_individual_ranef, as.data.frame(ranef(m_joint_answer))[,5:6]) #Slope

#Adding fixed effects to random effect
pooling_joint_fixef <- as.data.frame(fixef(m_joint_answer)) #Making data frame of fixed effects

pooling_joint$Intercept_ranef_fixef_estimate_answer <- pooling_joint_ranef[, 1] + pooling_joint_fixef[1, 1] #Adding fixef of intercept to ranef of intercept

pooling_joint$Slope_ranef_fixef_estimate_answer <- pooling_joint_ranef[, 3] + pooling_joint_fixef[1, 2] #Adding fixef of slope to ranef of slope

#CORRECT
#Saving random effect for individual 
pooling_individual_ranef <- as.data.frame(ranef(m_p_c))[,1:2] #Slope

#Adding fixed effects to random effect
pooling_individual_fixef <- as.data.frame(fixef(m_p_c)) #Making data frame of fixed effects

pooling_individual$Slope_ranef_fixef_estimate_correct <- pooling_individual_ranef[, 1] + pooling_individual_fixef[1, 1] #Adding fixef of slope to ranef of slope


#Adding rownames
pooling_joint <- cbind(Row.Names = rownames(pooling_individual_ranef), as.data.frame(pooling_individual))

write.csv(pooling_individual, file = "pooling_individual.csv")
```

#Calculating performance difference

```{r equality bias, ikke opdateret}
#create best and worst columns
Results$best <- ifelse(Results$Est_dif_blue_left > Results$Est_dif_blue_right, Results$Est_dif_blue_left, Results$Est_dif_blue_right )
Results$worst <- ifelse(Results$Est_dif_blue_left < Results$Est_dif_blue_right, Results$Est_dif_blue_left, Results$Est_dif_blue_right )
#create equality bias column
Results$eb <- Results$best/Results$worst
```

#Regression for difficulty
```{r regression for difficulty}
#regression for difficulty left 
get_prior(Correct ~ dif_blue_abs, data = ldata)

 prior =  c(
  prior(normal(0,2), class = "Intercept"), #How to motiavte this?
  prior(normal(0,2), class = "sigma"), #Roughly on the same scale
  prior(normal(0,2), class = "b"), #How to motiavte this?
  prior(normal(0,1), class = "b", coef = "dif_blue_abs"))
  
#Making the model, individual
dif_reg <- brm(
    Correct ~ dif_blue_abs + (1|unique),
    data = ldata,
    prior = prior,
    family = "bernoulli", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
    ) 
summary(dif_reg_left)
marginal_effects(dif_reg_left)

#Making the model, joint
dif_reg_joint <- brm(
    Correct_joint ~ dif_blue_abs + (1|GroupNumber),
    data = ldata,
    prior = prior,
    family = "gaussian", #As we had a binary outcome, we set this to "bernoulli"
    seed = 123 # Adding a seed makes results reproducible.
    ) 
summary(dif_reg_joint)
marginal_effects(dif_reg_joint)
```



```{r spagetti plot}

summary(m_p)

plot(m_p, pars = "^b_") 

plot(m_p)
```

- logistic regression individuals and joint - plot 
- calculate equality bias (best/worst)
- calculate collaborative bias (joint/best)